\documentclass[11pt]{amsart}
\usepackage{amssymb,amsbsy,upref,epsf,MnSymbol}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,mathtools,mathrsfs,wrapfig}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{enumerate}
%\usepackage{enumitem}



%-------------------------------------------<commands>--------------------------------------------------------
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Prj}{\mathbb{P}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\A}{\mathbb{A}}
\newcommand{\Four}{\mathcal{F}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\E}{\mathcal{E}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\eps}{\varepsilon}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\chevron}[1]{\langle #1 \rangle}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\bracket}[1]{\left[ #1 \right]}
\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\convex}{conv}
\DeclareMathOperator{\image}{Im}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\trace}{tr}
\DeclareMathOperator{\lspan}{span}
\DeclareMathOperator{\conv}{conv} % stands for conv, as in convex hull
\DeclareMathOperator{\Int}{int} % stands for int, as in interior of a set
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\ran}{ran}
\DeclareMathOperator{\rank}{rank}
%\DeclareMathOperator{\dim}{dim}
\newcommand{\dom}{\operatorname{dom}}
\newcommand{\cod}{\operatorname{cod}}
\newcommand{\Hom}{\operatorname{hom}}
\newcommand{\Ob}{\operatorname{Ob}}
\newcommand{\cl}{\operatorname{cl}}
\DeclareMathOperator{\BMO}{BMO}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\del}{\partial}
\newcommand{\pvec}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\grad}{\nabla}
\newcommand{\ddt}{\frac{d}{dt}}
\renewcommand{\div}{\operatorname{div}}
\newcommand{\Laplace}{\Delta}
\newcommand{\kinet}{\bracket{\del_t + v\cdot \grad_x}}
\newcommand{\bessel}{\paren{1-\Laplace_v}}
\newcommand{\loc}{\text{loc}}
\newcommand{\Lip}{\text{Lip}}
%\newcommand{\BMO}{\text{BMO}}
\renewcommand{\Re}{\operatorname{Re}}
\newcommand{\ddz}{\frac{d}{dz}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\twoheadrightarrow}
\newcommand{\isom}{\cong}
\newcommand{\rest}{{\upharpoonright}}
\newcommand{\weakly}{\rightharpoonup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ith}{^\mathrm{th}}
\newcommand{\n}{^{-1}}
\newcommand{\half}{\frac{1}{2}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\indic}[1]{\chi_{\{#1\}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newcommand{\eigen}[1]{\eta_{#1}} %my eigenfunctions
\newcommand{\Ctest}{C_c^\infty}
\newcommand{\test}{\mathcal{D}}

\newcommand{\ulow}{u_\ell}
\newcommand{\uhigh}{u_h}
\newcommand{\ulowth}[1]{\ulow^{#1}}
\newcommand{\uhighth}[1]{\uhigh^{#1}}

\newcommand{\HD}{\mathcal{H}}
\newcommand{\HDint}[2]{\int \abs{\Lambda^{#1} #2}^2}
\newcommand{\HDinth}[1]{\HDint{1/2}{#1}}

\newcommand{\Cgamma}{C_g}
\newcommand{\Comega}{C_\Omega}

\newcommand{\Rom}[1]{\MakeUppercase{\romannumeral #1}}

\newcounter{step_count}[section]
\newcommand{\step}[1]{\stepcounter{step_count} \smallskip \noindent{\textbf{Step \arabic{step_count}:} #1}}


%-------------------------------------------</commands>--------------------------------------------------------

%\newcommand{\draftnum}{1}%-----------------------------UPDATE DRAFT NUM----------------------------------------

\title[Boundary Regularity for SQG]{Holder regularity up to the boundary for critical SQG on bounded domains}

\author[Stokols]{Logan F. Stokols} 
\address[L. F. Stokols]{\newline Department of Mathematics, \newline The University of Texas at Austin, Austin, TX 78712, USA}
\email{lstokols@math.utexas.edu}

\author[Vasseur]{Alexis F. Vasseur}
\address[A. F. Vasseur]{\newline Department of Mathematics, \newline The University of Texas at Austin, Austin, TX 78712, USA}
\email{vasseur@math.utexas.edu}

\date{\today}

\subjclass[2010]{35Q35,35Q86}
%Logan: think about keyword for Japanese thing
\keywords{SQG, Bounded domain, Besov spaces on bounded domains, H\"older regularity,  De Giorgi method}

%\thanks{\textbf{Acknowledgment.} This work was partially supported by the NSF Grant DMS 1614918. }

\begin{document}

\begin{abstract}
We consider the dissipative SQG equation in bounded domains, first introduced in (Constantin Ignatova]. We show global Holder regularity up to the boundary of the solution. The method is based on the De Giorgi techniques as in [Caffarelli Vasseur]. The boundary introduces several difficulties, as the lack of translation invariance of the Laplacian operator, or the fact that the gradient does not commute with the Dirichlet Laplacian. 
\end{abstract}


\maketitle \centerline{\date}

\tableofcontents
The surface quasigeostrophic equation (SQG) is a special case of the quasi-geostrophic equation (QG) when the atmosphere is at rest. The (QG) model is used extensively in meteorology and oceanography [citations]. These models are described in \cite{Pe}. The SQG model was popularized by Constantin, Majda and Tabak in [citation], due to its similarities with the Euler and Navier-Stokes  equation. They proposed it as a toy model for the study of 3D Fluid equations (see also Held, Garner, Pierrehumbert, and Swanson \cite{GaHePiSw}). 

\vskip0.3cm
 We consider in this paper  critical SQG on a bounded domain. We will focus on the the following model, which was introduced by Constantin and Ignatova in \cite{CoIg.fraclap} and \cite{CoIg.sqg}.
 Consider  $\Omega$ a connected bounded domain in $\R^2$ with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$, and   the Laplacian with homogeneous Dirichlet boundary conditions $(-\Laplace_D)$.  If $(\eigen{k})_{k \in \N}$ is a family of eigenfunctions of $-\Laplace_D$ with corresponding eigenvalues $\lambda_k$ listed in increasing order, define
\[ \Lambda f := \sum_{k=0}^\infty \sqrt{\lambda_k} \chevron{f,\eigen{k}}_{L^2(\Omega)} \eigen{k}. \]
The critical SQG problem on $\Omega$ with initial data $\theta_0 \in L^2(\Omega)$ is
\begin{equation} \label{eq:main nonlinear} \begin{cases}
\del_t \theta + u\cdot \grad \theta + \Lambda \theta = 0 & (0,T) \times \Omega,
\\ u = \grad^\perp \Lambda\n \theta & [0,T] \times \Omega,
\\ \theta = \theta_0 & \{0\} \times \Omega.
\end{cases} \end{equation}

In the model, the dissipation $\Lambda =\Delta_D^{1/2}$  is due to the  Ekman pumping, while the nonlinear velocity $u$ comes from the geostrophic and hydrostatic balance (see \cite{Pe}).

The main result of this paper is the following.
\begin{theorem} \label{thm:main continuity}
Let $\theta$ be a smooth solution to \eqref{eq:main nonlinear} with initial data $\theta_0 \in L^2(\Omega)$ on a bounded open set $\Omega \subseteq \R^2$ with $C^{2,\beta}$ boundary, $\beta \in (0,1)$, and on a time interval $[0,T]$.  

Then for any $t \in (0,T)$, $\theta$ is bounded and H\"{o}lder continuous uniformly on $(t,T)\times\bar{\Omega}$.  
\vskip0.3cm

More precisely, there exists a constant $C$ depending only on $\Omega$ and $t$ such that
\[ \norm{\theta}_{L^\infty([t,T]\times\bar{\Omega})} \leq C \norm{\theta_0}_{L^2(\Omega)} \]
and there exists $\alpha \in (0,1)$ depending on $\Omega$, $t$, and $\norm{\theta_0}_{L^2(\Omega)}$ such that
\[ \norm{\theta}_{C^\alpha([t,T]\times\bar{\Omega})} \leq C \norm{\theta_0}_{L^2(\Omega)}. \]

%More precisely, there exists $\alpha \in (0,1)$ depending only on $\Omega$ and $\norm{\theta_0}_{L^2(\Omega)}$, and some constant $C$ depending only on $\Omega$ and $t$, such that
%\[ \norm{\theta}_{C^\alpha((t,T)\times\Omega)} \leq C \norm{\theta_0}_{L^2(\Omega)}. \]
\end{theorem}

This model was first thoroughly studied in the cases without boundaries (either $\R^2$ or the torus $\T^2$).   
Global weak solutions were first constructed in Resnick [Resnick]. Global regularity was first showed with small initial values [Constantin Cordoba, Wu], or extra $C^\alpha$ regularity on the velocity [Constantin Wu, Dong Pavlovic]. in [citation] Kiselev, Nazarov and Volberg showed the 
propagation of $C^\infty$ regularity. The global $C^\infty$ regularity for any $L^2$ initial values was first proved in  \cite{CaVa.sqg} (see also [Kiselev-Nazarov] Constantin Vicol \cite{CoVi}).   

\vskip0.3cm

In the presence of boundaries, there are several  distinct ways to define SQG. This can be attributed  to alternative definitions of the half-Laplacian.  Kriventsov [citation, Dennis Kriventsov] considered a two-phase problem which satisfied SQG only in a region, and was able to prove H\"{o}lder regularity in the time-independent case.  This problem, intended to model air currents over a region containing both land and water, contains a half-Laplacian and a Riesz transform defined, not spectrally, but in terms of extension.  In [citation, Matt and Vasseur], the authors derived from the Euler-Coriolis-Boussinesq model,   the full 3D inviscid quasigeostrophic system in an impermeable cylinder (see also [MV2] for the construction of small time smooth solutions to the model).  They obtain the natural boundary conditions in this case. It is noteworthy to mention that these boundary conditions lead a distinct set of boundary conditions for  SQG  than the one introduced in  \cite{CoIg.fraclap}  \cite{CoIg.sqg} and described above. 
However, due to the complexity of the model described in [MV], we focus in this paper only on the homogenous case.

\vskip0.3cm
Existence of weak solutions for (\ref{eq:main nonlinear})  is proven in \cite{CoIg.fraclap}. The interior regularity of solutions  is proven in \cite{CoIg.fraclap} (together with propagation of $L^\infty$ bounds).  The method of proof for interior regularity uses the  nonlinear maximum principles, introduced in [Constantin Vicol].   However, the bounds obtained in that paper  blow up near the boundary and do not provide global regularity up to the boundary.
  In \cite{CoIg.sqg} Remark 1, questions about   global regularity are suggested as  open problems.  Both the $C^\alpha(\bar{\Omega})$ regularity,  and the bootstrapping to the  $C^\infty(\bar{\Omega})$ regularity are mentioned as open problems.  %To quote Remark 1, these questions are unsolved ``due to the fact that the commutator between normal derivatives and the fractional Dirichlet Laplacian is not controlled uniformly up to the boundary.''  
  Our  result answers the first question, by  showing  that solutions $\theta$ to (\ref{eq:main nonlinear}) are globally H\"{o}lder continuous.
  Bootstrapping to $\C^\infty$ involves different techniques, and will be studied in a forthcoming  paper \cite{StVa.higher}.  
\vskip0.3cm

Our proof is based on  the De Giorgi method \cite{DG}.  The method was applied to the SQG problem first in \cite{CaVa.sqg}.  The method is powerful to show $C^\alpha$ regularity to nonlocal equations (see Caffarelli-Chan-Vasseur). It has been applied in a variety of situations for non-local problems, as the 3D Quasigeostrophic problem \cite{NoVa.qg},   the time-fractional case (Allen Caffarelli Vasseur), the kinetic setting (Silvestre- Imbert, Stokols -Vasseur), or even more exotic situations as the Hamilton-Jacobi equations (see Chan Vasseur, Stokols-Vasseur).  
\vskip0.3cm

 The first broad  idea consists in decoupling the  velocity $u$ from  $\theta$ to work on  a linear equation, and prove alternating regularity results for $\theta$ and $u$ independently.  We first show that $\theta$ is in $L^\infty$ regardless of the value of $u$ (Section~\ref{sec:Linfty}). The idea is to prove a decrease-in-oscillation lemma for fractional diffusion equations with  drift (Section~\ref{sec:harnack}).  By applying this oscillation lemma, then scaling our equation, and then applying the oscillation lemma again iteratively, we can show that $\theta$ is H\"{o}lder continuous (Section~\ref{sec:holder}).  
\vskip0.3cm

However, for this, we need to obtain scaling invariant controls on the drift   $u = \grad \Lambda^{-1} \theta$ (Section~\ref{sec:littlewood paley}).  Though $L^\infty$ is the obvious choice, since solutions to SQG are easily shown to be $L^\infty$ bounded under minimal assumptions, the Riesz transform is not bounded from $L^\infty$ to $L^\infty$.  The usual solution is to consider $\BMO$ (as in \cite{CaVa.sqg} and \cite{NoVa.qg}), but in the case of bounded domains the Riesz transform is not known to be bounded in this space either.  The idea is to use extensions of the littlewood-Paley theory to bounded domains. 

The adaptation of Fourier analysis and Littlewood-Paley theory to Schrodinger operators has is a well-studied subject [citations].  As an application of this theory, \cite{IMTs} and [citation, Dong et al] have considered operators defined on open subsets of $\R^n$, which includes as a special case the operator $-\Delta_D$ (a Schrodinger operator with zero potential).  In particular, in \cite{IMTb},  Iwabuchi, Matsuyama, and Taniguchi derives many important results, including the Bernstein inequalities, for Besov spaces adapted to the operator $-\Laplace_D$ on bounded open subsets of $\R^n$ with smooth boundary.  This theory turns out to greatly improve our understanding of the Riesz transform $\grad \Lambda^{-1}$ on bounded domains.  


Using the results of \cite{IMTb}, we will be able to show that the Riesz transform of an $L^\infty$ function whose Fourier decomposition $f = \sum f_k \eigen{k}$ is supported on high frequencies $k > N$ will be bounded in the weak sobolev space $W^{-1/4,\infty}$, and the Riesz transform of an $L^\infty$ function whose Fourier decomposition is supported on low frequencies $k<N$ will have bounded Lipschitz constant.  The cutoff $N$ for dividing high frequencies from low frequencies must depend however on the size of the domain $\Omega$.  In the case of $\R^2$, where $\grad$  and $\Lambda^{-1}$ commute, this is equivalent to the observation that the Riesz transform is bounded from $L^\infty$ to the Besov space $B_{\infty,\infty}^0$.  In the case of bounded domains, the argument must be more subtle.  We must decompose $\theta$ into its Littlewood-Paley projections, individually bound the Riesz transform of each projection in multiple spaces, and then recombine these infinitely-many functions into a low-frequency collection and a high-frequency collection depending on the scale of oscillation we are trying to detect.  

We make this notion precise with the following definition.  

\begin{definition}[Calibrated sequence] \label{def:calibrated}
Let $\Omega\subseteq \R^2$ be any bounded open set and $0<T\in\R$.  We call a function $u\in L^2([0,T]\times\Omega)$ \textbf{calibrated} if it can be decomposed as the sum of a calibrated sequence
\[ u = \sum_{j \in \Z} u_j \]
with each $u_j \in L^2([0,T]\times\Omega)$ and the infinite sum converging in the sense of $L^2$.  

We call a sequence $(u_j)_{j\in\Z}$ \textbf{calibrated} for a constant $\kappa$ and a center $N$ if each term of the sequence satisfies the following bounds.  

\begin{align*}
\norm{u_j}_{L^\infty([0,T]\times\Omega)} &\leq \kappa, \\
\norm{\grad u_j}_{L^\infty([0,T]\times\Omega)} &\leq 2^{j} 2^{-N} \kappa, \\
\norm{\Lambda^{-1/4} u_j}_{L^\infty([0,T]\times\Omega)} &\leq 2^{-j/4} 2^{N/4} \kappa.  
\end{align*} 

\end{definition}

In Section \ref{sec:littlewood paley} we will show that $u$ is calibrated and in Section \ref{sec:holder} we will show that it remains calibrated at all scales (specifically, with fixed constant $\kappa$ but not always with the same center $N$).  Therefore we will consider the linear equation
\begin{equation} \label{eq:main linear} \begin{cases}
\del_t \theta + u \cdot \grad \theta + \Lambda \theta = 0, & [-T,0]\times\Omega \\
\div u = 0 & [-T,0]\times\Omega.
\end{cases} \end{equation}





In Section \ref{sec:Linfty} we show that solutions to \eqref{eq:main linear}, with minimally regular velocity and $L^2$ initial data, become $L^\infty$ instantly, and in Sections \ref{sec:de giorgi} and \ref{sec:harnack} we will show that solutions to \eqref{eq:main linear} with calibrated velocity have decreasing oscillation between scales.  


 Previous applications of the De Giorgi method to equations related to (\ref{eq:main linear}) generally make extensive use of either an extension representation (c.f. \cite{CaVa.sqg}) or a singular-integral representation (c.f. \cite{NoVa.qg}).  In this paper, we  use the kernel representation of  the Dirichlet fractional Laplacian  derived by Caffarelli and Stinga \cite{CaSt}. It is an generalization of   [citation Stinga Torrea] and \cite{CaSt} the extension representation of [citation Caff Silvestre]. 
 This theory is pivotal in translating the existing non-local De Giorgi techniques to the problem at hand(see Section~\ref{sec:lemmas}).  


%In [citation Stinga Torrea] and \cite{CaSt} the extension representation of [citation Caff Silvestre] is applied to the Dirichlet fractional Laplacian, and in \cite{CaSt} this representation is used to derive a singular integral representation for $\Lambda^s$. 



%Though it is beyond the scope of the present paper, we believe that global regularity of solutions to \eqref{eq:main nonlinear} can be proven once H\"{o}lder regularity is known.  In appendix 2 of \cite{CoIg.sqg}, local-in-time existence of solutions to \eqref{eq:main nonlinear} with $\theta \in L^\infty(0,t; L^2(\Omega) \cap H_0^1(\Omega) \cap L^4(\Omega))$ and $u \in L^\infty(0,t; L^4(\Omega))$ is proven for initial data sufficiently smooth.  Therefore, going forward, we can assume this much regularity on our solutions.  

\textbf{Notation.} Throughout the paper, we will use the following notations.
%\textbf{Notation.}
If $f = \sum_k f_k \eigen{k}$ then
\begin{align*} 
\norm{f}_{\HD^s} &:= \paren{\sum_k \lambda_k^{s} f_k^2}^{1/2} 
\\ &= \HDint{s}{f}. 
\end{align*}
We suppress the dependence on $\Omega$, though in fact the $\lambda_k$ and $\Lambda$ are defined in terms of the domain $\Omega$.  The relevant domain will be clear from context.  This is in fact a norm, not a seminorm, since $\norm{f}_{L^2(\Omega)} \leq \lambda_0^{s/2} \norm{f}_{\HD^s}$.  

For a set $D$ and a function $f:A \to \R$, denote
\begin{align*}
\bracket{f}_{\alpha;D} &:= \sup_{x,y \in D, x \neq y} \frac{|f(x)-f(y)|}{|x-y|^\alpha},  &\alpha \in (0,1], \\
\norm{f}_{C^\alpha(D)} &:= \norm{f}_\infty + \bracket{f}_{\alpha;D}, & \alpha \in (0,1], \\
\norm{f}_{C^{k,\alpha}(D)} &:= \sum_{n=0}^k \norm{D^n f}_\infty + \bracket{D^k f}_{\alpha;D}, & \alpha \in (0,1], k \in \N.
\end{align*}
When the domain $D$ is ommited, the relevant spatial domain $\Omega$ is implied.  

We will use the notation $(x)_+ := \max(0,x)$.  When the parentheses are ommited, the subscript~$+$ is merely a label.  
Throughout this paper, if an integral sign is written $\int$ without a specified domain, the domain is implied to be $\Omega$, with $\Omega$ defined in context.  
For any vector $v = (v_1,v_2)$, by $v^\perp$ we mean $(-v_2,v_1)$, and by $\grad^\perp$ we mean $(-\del_y, \del_x)$.  

The symbol $C$ represents a constant which may change value each time it is written.  
\vskip0.3cm

The Paper is organized as follows. Section \ref{sec:lemmas} is dedicated to the properties of $\Lambda$.....



\section{Properties of $\Lambda$} \label{sec:lemmas}

We begin by recounting the result of \cite{CaSt} which gives us a singular integral representation of the $\HD^s$ norm.  
\begin{proposition}[Caffarelli-Stinga Representation] \label{thm:Caff Stinga representation}
Let $s \in (0,1)$ and $f,g \in \HD^{s}$ on a bounded $C^{2,\alpha}$ domain $\Omega \subseteq \R^2$.  Then
\[ \int_\Omega \Lambda^s f \Lambda^s g \,dx = \iint_{\Omega^2} [f(x)-f(y)][g(x)-g(y)] K_{2s}(x,y) \,dxdy + \int_{\Omega} f(x) g(x) B_{2s}(x) \,dx \]
for kernels $K_{2s}$ and $B_{2s}$ which depend on the parameter $s$ and the domain $\Omega$.  

Moreover, these kernels are bounded
\[ 0 \leq K_{2s}(x,y) \leq \frac{C(\Omega,s)}{|x-y|^{2+2s}} \]
for all $x \neq y \in \Omega$ and
\[ 0 \leq B_{2s}(x) \]
for all $x \in \Omega$.  

Finally, for any $s,t \in (0,2)$ there exists a constant $c = c(s,t,\Omega)$ such that for all $x\neq y \in \Omega$
\begin{equation} \label{relationship Kt and Ks} K_{t}(x,y) \leq |x-y|^{s-t} K_{s}(x,y). \end{equation}
\end{proposition}

\begin{proof}
See \cite{CaSt} Theorems 2.3 and 2.4.  

Theorem 2.4 in \cite{CaSt} does not explicitly state the result \eqref{relationship Kt and Ks}.  However, it does state that for each kernel $K_s$ there exists a constant $c_s$ dependent on $s$ and $\Omega$ such that 
\[ \frac{1}{c_s} |x-y|^{2+s} K_s(x,y) \leq \min\paren{1,\frac{\eigen{0}(x)\eigen{0}(y)}{|x-y|^2}} \leq c_s |x-y|^{2+s} K_s(x,y). \]
Since the middle term does not depend on $s$, we can say that
\[ |x-y|^{2+t} K_t(x,y) \leq c_t c_s |x-y|^{2+s} K_s(x,y) \]
from which \eqref{relationship Kt and Ks} follows.  
\end{proof}

From the explicit formulae given in \cite{CaSt}, we see that $K_{2s}$ is roughly equal to the standard kernel for the $\R^2$ fractional Laplacian $(-\Laplace)^s$ when both $x$ and $y$ are in the interior of $\Omega$ or when $x$ and $y$ are extremely close together, but decays to zero when one point is in the interior and the other is near the boundary.  The kernel $B_{2s}$ is well-behaved in the interior but has a singularity at the boundary $\del \Omega$.  This justifies our thinking of the $K_{2s}$ term as the interior term and $B_{2s}$ as a boundary term.  

When comparing the computations in this paper to corresponding computations on $\R^2$, it is convenient to say that the interior term behaves roughly the same as in the unbounded case, while the boundary term behaves roughly like a lower order term (in the sense that it is easily localized).  

Many useful results can be derived from Caffarelli-Stinga representation formula, including the following:

\begin{lemma} \label{thm:Lambda stuff}
Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary.  

\begin{enumerate}[(a)]
\item \label{thm:disjoint} Let $s \in (0,1)$.  If $f$ and $g$ are non-negative functions with disjoint support (i.e. $f(x)g(x) = 0$ for all $x$), then 
\[ \int \Lambda^s f \Lambda^s g \,dx \leq 0. \]

\item \label{thm:product rule} Let $s \in (0,1)$.  If $g \in C^{0,1}(\Omega)$ then
\[ \norm{fg}_{\HD^s} \leq 2 \norm{g}_\infty \norm{f}_{\HD^s} + 2 \norm{f}_2 \sup_y \int \frac{|g(x)-g(y)|^2}{|x-y|^{2+2s}} \,dx. \]

\item \label{thm:extra product rule} Let $s \in (0,1)$.  If $g \in C^{0,1}(\Omega)$ then for some constant $C=C(s)$
\[  \norm{fg}_{\HD^s} \leq C \norm{g}_{C^{0,1}(\Omega)} \paren{\norm{f}_2 + \norm{f}_{\HD^s}}. \]

\item \label{thm:L1 of Lambda bounded} Let $s\in(0,1/2)$.  Let $g$ an $L^\infty(\Omega)$ function and $f \in \HD^{2s}$ be non-negative with compact support.  Let there be a constant $\Comega$ such that
\begin{equation} \label{K bounded between orders} K_s(x,y) \leq \Comega |x-y|^{3s} K_{4s}(x,y). \end{equation}

Then
\[ \int \Lambda^{s/2} g \Lambda^{s/2} f \leq C \norm{g}_\infty |\supp(f)|^{1/2} \paren{ \norm{f}_2 + \norm{f}_{\HD^{2s}}}. \]

\item \label{thm:L1 of Lambda1/4 bounded} Let $g$ an $L^\infty(\Omega)$ function and $f \in \HD^{1/2}$ be non-negative with compact support.  Let there be a constant $\Comega$ such that
\[ K_{1/4}(x,y) \leq \Comega |x-y|^{3/4} K_{1}(x,y). \]

Then
\[ \int g \Lambda^{1/4} f \leq C \norm{g}_\infty |\supp(f)|^{1/2} \paren{ \norm{f}_2 + \norm{f}_{\HD^{1/2}}}. \]

\end{enumerate}
\end{lemma}

\begin{proof}
We prove these corollaries one at a time.  

\textbf{Proof of \eqref{thm:disjoint}:}
From Proposition \ref{thm:Caff Stinga representation}
\[ \int \Lambda^s f \Lambda^s g \,dx = \iint [f(x)-f(y)][g(x)-g(y)] K(x,y) \,dxdy + \int f(x) g(x) B(x) \,dx. \]

Since $f$ and $g$ are non-negative and disjoint, the $B$ term vanishes.  Moreover, the product inside the $K$ term becomes
\[ [f(x)-f(y)][g(x)-g(y)] = -f(x)g(y)-f(y)g(x) \leq 0. \]
Since $K$ is non-negative, the result follows.  

\textbf{Proof of \eqref{thm:product rule}:}
From Proposition \ref{thm:Caff Stinga representation}
\[ \int |\Lambda^s (fg)|^2 = \iint \paren{g(x)[f(x)-f(y)] + f(y)[g(x)-g(x)]}^2 K + \int f^2 g^2 B \]
\[ \leq 2 \norm{g}_\infty^2 \norm{f}_{\HD^s}^2 + 2 \int f(y)^2 \int \frac{|g(x)-g(y)|^2}{|x-y|^{2+2s}}. \]

\textbf{Proof of \eqref{thm:extra product rule}:}
This follows immediately from \eqref{thm:product rule}.  

\textbf{Proof of \eqref{thm:L1 of Lambda bounded}:}
From Proposition \ref{thm:Caff Stinga representation} we can decompose
\[ \int \Lambda^{s/2} g \Lambda^{s/2} f = \Rom{1}_< + \Rom{1}_\geq + \Rom{2} \]
where
\begin{align*} 
\Rom{1}_< &:= \iint_{|x-y| < 1} [g(x)-g(y)][f(x)-f(y)] K_s, \\
\Rom{1}_\geq &:= \iint_{|x-y|\geq 1} [g(x)-g(y)][f(x)-f(y)] K_s, \\
\Rom{2} &:= \int f g B_s. 
\end{align*}

First we estimate $\Rom{1}_<$.  From \eqref{K bounded between orders} and from the symmetry of the integrand and the fact that $[f(x)-f(y)]$ vanishes unless at least one of $f(x)$ or $f(y)$ is non-zero,
\[ \abs{\Rom{1}_<} \leq 2 \iint_{|x-y| < 1} \indic{f > 0}(x) \abs{g(x)-g(y)} \cdot \abs{f(x)-f(y)} \cdot |x-y|^{3s} K_{4s}. \]
We can break this up by Holder's inequality
\[ \abs{\Rom{1}_<} \leq 2 \paren{\iint_{|x-y| < 1} \indic{f > 0}(x) [g(x)-g(y)]^2 |x-y|^{6s} K_{4s} }^{1/2} \paren{\iint [f(x)-f(y)]^2 K_{4s} }^{1/2}. \]
The kernel $|x-y|^{6s} K_{4s} \indic{|x-y| < 1}$ is integrable in $y$ for $x$ fixed.  Therefore
\begin{equation} \label{K near of L1 less than L2 stuff} \abs{\Rom{1}_<} \leq 2 \paren{ 2\norm{g}_\infty^2 \int C \indic{f > 0}(x) \,dx }^{1/2} \paren{ \norm{f}_{\HD^{2s}}^2}^{1/2}. \end{equation}

For the term $\Rom{1}_\geq$, by the symmetry of the integrand we have
\[ \abs{\Rom{1}_\geq} \leq  2\norm{g}_\infty 2\int |f(x)| \int_{|x-y|\geq 1} K_s(x,y)dy \,dx. \]
Since $K_s \indic{|x-y|\geq 1}$ is integrable in $y$ for $x$ fixed,
\begin{equation} \label{K far of L1 less than L2 stuff}
\abs{\Rom{1}_\geq} \leq C \norm{g}_\infty \norm{f}_1.  
\end{equation}

For the boundary term \Rom{2}, 
\[ \abs{\Rom{2}} \leq \norm{g}_\infty \int\indic{f>0} f B_s. \]
Since $f \geq 0$, $[f(x)-f(y)][\indic{f > 0}(x) - \indic{f > 0}(y)] \geq 0$.  Therefore
\[ \int \indic{f > 0} f B_s \leq \int \Lambda^{s/2} \indic{f>0} \Lambda^{s/2} f = \int \indic{f>0} \Lambda^{s} f. \]
Applying H\"{o}lder's inequality, we arrive at
\[ \abs{\Rom{2}} \leq \norm{g}_\infty |\supp(f)|^{1/2} \norm{f}_{\HD^{s}}. \]
This combined with \eqref{K near of L1 less than L2 stuff} and \eqref{K far of L1 less than L2 stuff} gives us 
\[ \int \Lambda^{s/2} g \Lambda^{s/2} f \leq C \norm{g}_\infty \paren{|\supp(f)|^{1/2} \norm{f}_{\HD^{2s}} + \norm{f}_1 + |\supp(f)|^{1/2} \norm{f}_{\HD^s}}. \]

The lemma follows since $\norm{f}_1 \leq |\supp(f)|^{1/2} \norm{f}_2$ and since $\norm{f}_{\HD^s} \leq \norm{f}_{L^2} + \norm{f}_{\HD^{2s}}$.  

\textbf{Proof of \eqref{thm:L1 of Lambda1/4 bounded}:}
This is an immediate application of part \eqref{thm:L1 of Lambda bounded}.  

\end{proof}

Let us consider the relationship between the norm $\HD^s$ and the classical $H^s$ norm.  

It is known (see \cite{CoIg.sqg} and \cite{CaSt}) that for $s \in (0,1)$ the spaces $\HD^s$ are equivalent to certain subsets of $H^s(\Omega)$ spaces defined in terms of the Gagliardo semi-norm.  In particular, we know that smooth functions with compact support are dense in $\HD^s$ and that elements of $\HD^s$ have trace zero for $s \in [\frac{1}{2},1]$.  

The most important fact for us is that the fractional Sobolev norms defined in terms of extension (for which we have access to a variety of theorems regarding compactness and Sobolev embeddings) are dominated by our $\HD^s$ norm with a constant that is independent of $\Omega$.  

Consider the extension-by-zero operator $E:L^2(\Omega) \to L^2(\R^2)$
\[ E f (x) = \begin{cases} f(x) & x \in \Omega, \\ 0 & x \in \R^2 \setminus \Omega. \end{cases} \]

\begin{proposition} \label{thm:hadamard 3 lines}
Let $\Omega \subseteq \R^2$ be any bounded open set with Lipschitz boundary.  For any $s \in [\frac{1}{2},1]$ and function $f \in \HD^s$,
\[ \int_{\R^2} \abs{\paren{-\Laplace}^{s/2} E f}^2 \leq \int_\Omega \abs{\Lambda^s f}^2. \]
Here $\paren{-\Laplace}^s$ is defined in the fourier sense.  
\end{proposition}

We will prove this proposition by interpolating between $s = 0$ and $s=1$.  Before we can do this, we must prove the same in the $s=1$ case.  

\begin{lemma} \label{thm:H1 and H1}
Let $\Omega \subseteq \R^2$ be any bounded open set with Lipschitz boundary.  For all functions $f$ in $\HD^1$,
\[ \int_\Omega \abs{\grad f}^2 = \int_\Omega \abs{\Lambda f}^2. \]
\end{lemma}

\begin{proof}
Let $\eigen{i}$ and $\eigen{j}$ be two eigenfunctions of the Dirichlet Laplacian on $\Omega$.  Note that these functions are smooth in the interior of $\Omega$ and vanish at the boundary, so we can apply the divergence theorem and find
\[ \int \grad \eigen{i} \cdot \grad \eigen{j} = - \int \eigen{i} \Laplace \eigen{j} = \lambda_j \int \eigen{i} \eigen{j} = \lambda_j \delta_{i=j}. \]
%Because $\Omega$ has Lipschitz boundary, and because $\eigen{i} \grad \eigen{j}$ is smooth on $\Omega$ and countinuous and bounded on $\overline{\Omega}$ vanishing on the boundary, therefore 
%\[ \int_\Omega \div(\eigen{i} \grad \eigen{j}) = \int_{\del \Omega} \eigen{i} \grad \eigen{j}. \]
%But $\eigen{i} \grad \eigen{j}$ vanishes on the boundary, so the right hand side vanishes.  Moreover, $\div(\eigen{i} \grad \eigen{j}) = \grad \eigen{i} \cdot \grad \eigen{j} + \eigen{i} \Laplace \eigen{j}$.  Therefore
%\[ \int \grad \eigen{i} \cdot \grad \eigen{j} = - \int \eigen{i} \Laplace \eigen{j} = \lambda_j \int \eigen{i} \eigen{j} = \lambda_j \delta_{i=j}. \]
%Of course, the inner product of two eigenfunctions is 0 unless they are the same eigenfunction, in which case it is 1.  

Consider a function $f = \sum f_k \eigen{k}$ which is an element of $\HD^1$, by which we mean $\sum \lambda_k f_k^2 < \infty$.  Since $\norm{\grad \eigen{k}}_{L^2(\Omega)} = \sqrt{\lambda_k}$, the following sums all converge in $L^2(\Omega)$ and hence the calculation is justified:
\begin{align*}
\int \abs{\grad f}^2 &= \int \paren{\sum_i f_i \grad \eigen{i} } \paren{\sum_j f_j \grad \eigen{j}}
\\ &= \int \sum_{i,j} (f_i f_j) \grad \eigen{i} \cdot \grad \eigen{j}
\\ &= \sum_{i,j} (f_i f_j) \int \grad \eigen{i} \cdot \grad \eigen{j}
\\ &= \sum_j \lambda_j f_j^2.
\end{align*}
From this the result follows.
\end{proof}


We come now to the proof of Proposition \ref{thm:hadamard 3 lines}.  
\begin{proof}
Let $g$ be any Schwartz function in $L^2(\R^2)$, and let $f$ be a function in $\HD^s$.  
%Let $E:\HD^1(\Omega) \to H^1(\R^2)$ be a the extension-by-zero operator, where $H^1$ denotes the classical Sobolev space defined using the gradient.  
Define the function
\[ \Phi(z) = \int_{\R^2} \paren{-\Laplace}^{z/2} g E \Lambda^{s-z} f, \qquad z \in \C, \Re(z) \in [0,1]. \]

Recall (see e.g. [citation Jerison, Kenig]) that when $t \in \R$, $(-\Laplace)^{i t}$ is a unitary transformation on $L^2(\R^2)$, and $\Lambda^{i t}$ is a unitary transformation on $L^2(\Omega)$.  

When $\Re(z) = 0$, then $\norm{\paren{-\Laplace}^{z/2} g}_2 = \norm{g}_2$ and $\norm{\Lambda^{s-z} f}_2 = \norm{f}_{\HD^s}$.  Hence
\[ \Phi(z) \leq \norm{g}_2 \norm{f}_{\HD^s}. \]

When $\Re(z)=1$, integrate by parts to obtain
\[ \Phi(z) = \int_{\R^2} \paren{-\Laplace}^{(z-1)/2} g  \paren{-\Laplace}^{1/2} E \Lambda^{s-z} f. \]
Then $\norm{\paren{-\Laplace}^{(z-1)/2} g}_2 = \norm{g}_2$, while $\norm{\Lambda^{s-z} f}_{\HD^1} = \norm{f}_{\HD^s}$.  As an $\HD^1$ function, $\Lambda^{s-z} f$ has trace zero so 
\[ \norm{\grad E \Lambda^{s-z} f}_{L^2(\R^2)} = \norm{\grad \Lambda^{s-z} f}_{L^2(\Omega)} = \norm{f}_{\HD^s}. \]
Of course $\norm{\paren{-\Laplace}^{1/2} \,\cdot\,}_{L^2(\R^2)} = \norm{\grad \,\cdot\,}_{L^2(\R^2)}$ in general so
\[ \Phi(z) \leq \norm{g}_2 \norm{f}_{\HD^s}. \]

In order to apply the Hadamard three-lines lemma, we must show that $\Phi$ is differentiable in the interior of its domain.  

Rewrite the integrand of $\Phi$ as
\[ \Four\n\paren{ |\xi|^z \hat{g} } E \sum_k \lambda_k^{\frac{s-z}{2}} f_k. \]
The derivative $\ddz$ commutes with linear operators like $\Four\n$ and $E$, so the derivative is
\begin{equation} \label{derivative of integrand} \Four\n\paren{ \ln(|\xi|) |\xi|^z \hat{g} } E \sum_k \lambda_k^{\frac{s-z}{2}} f_k + \Four\n\paren{ |\xi|^z \hat{g} } E \sum_k \frac{-1}{2} \ln(\lambda_k) \lambda_k^{\frac{s-z}{2}} f_k. \end{equation}

Fix some $z \in \C$ with $\Re(z) \in (0,1)$.  Since $g$ is a Schwartz function, $\ln(|\xi|)|\xi|^z \hat{g}$ is in $L^2$.  Moreover, for any $\eps>0$ we have $\ln(\lambda_k) \lambda_k^{\frac{s-z}{2}} \leq C \lambda_k^{\frac{s-z+\eps}{2}}$ for some $C$ independent of $k$ but dependent on $z$, $\eps$.  Take $\eps < \Re(z)$ and, since $f \in \HD^{s}$, this sum will converge in $L^2$.  

The differentiated integrand \eqref{derivative of integrand} is therefore a sum of two products of $L^2$ functions.  In particular it is integrable, which means we can interchange the integral sign and the derivative $\ddz$ and prove that $\Phi'(z)$ is finite for all $0<\Re(z)<1$. 

By the Hadamard three-lines lemma, for any $z \in (0,1)$ we have $\Phi(z) \leq \norm{g}_2 \norm{f}_{\HD^s}$.  
Evaluating $\Phi(s)$, we see
\[ \int_{\R^2} \paren{-\Laplace}^{s/2} g E f \leq \norm{g}_{L^2(\R^2)} \norm{f}_{\HD^s}. \]
This inequality holds for any Schwartz function $g \in L^2(\R^n)$ and any $f \in \HD^{s}$,

Since Schwartz functions are dense in $L^2(\R^2)$, the proof is complete.  
\end{proof}



%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------



\section{$L^\infty$ bounds for $\theta$} \label{sec:Linfty}

Our goal in this section is to show that the $L^\infty$ norm of solutions to \eqref{eq:main linear} are instantaneously bounded by the $L^2$ norm of the initial data.  Note that global $L^\infty$ bounds for $L^\infty$ initial data are proven in \cite{CoIg.sqg}.  

\begin{proposition}[$L^2$ to $L^\infty$] \label{thm:L2 to Linfty}
Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$, and $T \in \R^+$ a positive time.  

Let $\theta \in L^\infty(0,T; L^4(\Omega)) \cap L^2(0,T; H^1(\Omega))$ and $u \in L^\infty(0,T; L^4(\Omega))$ solve \eqref{eq:main linear} in the sense of distributions with $\theta_0 \in L^2(\Omega)$.  

Then for any time $S \in (0,T)$ there exists a constant $C = C(S)$ such that
\[ \norm{\theta}_{L^\infty([S,T]\times \Omega)} \leq C \norm{\theta_0}_{L^2(\Omega)}. \]
\end{proposition}

In order to prove this proposition, we require an energy inequality for $(\theta-C)_+$ for arbitrary constants $C$.  We will prove a much more general lemma, which has further applications in Section~\ref{sec:de giorgi}.  

\begin{lemma}[Caccioppoli Estimate] \label{thm:caccioppoli}
Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$, and $T \in \R^+$ a positive constant.  Let $\Psi: [-T,0]\times \Omega \to \R$ be non-negative and smooth, and $\gamma < 1/2$.  Then there exists a constant $C$ depending on $\norm{\grad \Psi}_\infty$ and $\sup_t \bracket{\Psi(t,\cdot)}_{\gamma; \Omega}$ such that the following holds:
\vskip0.3cm

Let $\theta \in L^\infty(0,T; L^4(\Omega)) \cap L^2(0,T;H^1(\Omega))$ and $u \in L^\infty(0,T; L^4(\Omega))$ solve \eqref{eq:main linear} in the sense of distributions.  Then the functions
\[ \theta_+ := \paren{\theta - \psi(\cdot-\Gamma)}_+, \qquad \theta_- := \paren{\psi(\cdot-\Gamma) - \theta}_+ \]
satisfy the inequlality
\[ \ddt \int \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2 - \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \theta_- \leq C \paren{ \int \indic{\theta_+ > 0} + \int \theta_+ (\del_t \Psi + u\cdot\grad\Psi) }. \]


\end{lemma}

\begin{proof}
We multiply \eqref{eq:main linear} by $\theta_+$ and integrate in space to obtain
\[ 0 = \int \theta_+ \bracket{ \del_t + u \cdot \grad + \Lambda } \paren{\theta_+ + \Psi - \theta_-} \]
which decomposes into three terms, corresponding to $\theta_+$, $\Psi$, and $\theta_-$.  We analyze them one at a time.  

Firstly,
\begin{align*} 
\int \theta_+ \bracket{ \del_t + u \cdot \grad + \Lambda } \theta_+ &= \paren{\frac{1}{2}} \ddt \int \theta_+^2 + (1/2) \int \div u \, \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2
\\ &= \paren{\frac{1}{2}} \ddt \int \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2.
\end{align*}

The $\Psi$ term produces important error terms:
\begin{align*} 
\int \theta_+ \bracket{ \del_t + u \cdot \grad + \Lambda } \Psi &= \int \theta_+ \del_t \Psi + \int \theta_+ u \cdot \grad \Psi + \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi
\\ &= \int \theta_+ (\del_t \Psi + u \cdot \grad \Psi) + \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi
\end{align*}

Since $\theta_+$ and $\theta_-$ have disjoint support, the $\theta_-$ term is nonnegative by Lemma~\ref{thm:Lambda stuff} part \eqref{thm:disjoint}:
\begin{align*} 
\int \theta_+ \bracket{ \del_t + u \cdot \grad + \Lambda } \theta_- &= \paren{\frac{1}{2}} \int \theta_+ \del_t \theta_- + \int \theta_+ u \cdot \grad \theta_- + \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \theta_-
\\ &= \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \theta_- \leq 0.
\end{align*}

Put together, we arrive at 
\begin{equation} \label{first form of cacciopolli} \paren{\frac{1}{2}} \ddt \int \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2 - \int \Lambda^{1/2}\theta_+ \Lambda^{1/2} \theta_- + \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi \leq \abs{\int \theta_+ (\del_t \Psi + u \cdot \grad \Psi)}. \end{equation}

At this point we break down the $\Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi$ term using the formula from Proposition~\ref{thm:Caff Stinga representation}.  
\[ \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi = \iint [\theta_+(x)-\theta_+(y)][\Psi(x)-\Psi(y)] K(x,y) + \int \theta_+ \Psi B. \]
Since $B \geq 0$ and $\Psi$ is non-negative by assumption, the $B$ term is non-negative and so
\begin{equation} \label{just the K cacciopolli} \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi \geq \iint [\theta_+(x)-\theta_+(y)][\Psi(x)-\Psi(y)] K(x,y). \end{equation}
The remaining integral is symmetric in $x$ and $y$, and the integrand is only nonzero if at least one of $\theta_+(x)$ and $\theta_+(y)$ is nonzero.  Hence
\[ \iint [\theta_+(x)-\theta_+(y)][\Psi(x)-\Psi(y)] K(x,y) \leq 2 \iint \indic{\theta_+>0}(x) \abs{\theta_+(x)-\theta_+(y)} \cdot \abs{\Psi(x)-\Psi(y)} K(x,y). \]
Now we can break up this integral using the Peter-Paul variant of H\"{o}lder's inequality, and since $\iint [\theta_+(x)-\theta_+(y)]K \leq \norm{\theta_+}_{\HD^{1/2}}^2$ the inequality \eqref{just the K cacciopolli} becomes
\begin{equation} \label{good lower bound on psi term cacciopoli}
\int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \Psi + \eps \int \abs{\Lambda^{1/2}\theta_+}^2 \geq - \frac{1}{\eps} \iint \indic{\theta_+>0}(x) [\Psi(x)-\Psi(y)]^2 K(x,y). 
\end{equation}
%\begin{equation} \label{K bdd by little bit of energy cacciopolli} \abs{\iint [\theta_+(x)-\theta_+(y)][\Psi(x)-\Psi(y)] K(x,y)} \leq \eps \int \abs{\Lambda^{1/2}\theta_+}^2 + \frac{1}{\eps} \iint \indic{\theta_+>0}(x) [\Psi(x)-\Psi(y)]^2 K(x,y). \end{equation}

It remains to bound the quantity $[\Psi(x)-\Psi(y)]^2 K(x,y)$.  By Proposition~\ref{thm:Caff Stinga representation}, there is a universal constant $C$ such that
\[ K(x,y) \leq \frac{C}{|x-y|^{3}}. \]
The cutoff $\Psi$ is locally Lipschitz, and H\"{o}lder continuous with exponent $\gamma < 1/2$, by assumption.  Therefore 
\[ [\Psi(x)-\Psi(y)]^2 K(x,y) \leq |x-y|^{-1} \wedge |x-y|^{2\gamma-3}. \]
Since $3-2\gamma > 2$, this quantity is integrable.  Thus
\[ \int \indic{\theta_+>0}(x) \int [\Psi(x)-\Psi(y)]^2 K(x,y) \,dydx \leq C(\norm{\grad \Psi}_\infty, \bracket{\Psi}_\gamma) \int \indic{\theta_+>0} \,dx. \]
Combining this with \eqref{first form of cacciopolli} and \eqref{good lower bound on psi term cacciopoli} we obtain
\[ \ddt \int \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2 - \int \Lambda^{1/2} \theta_+ \Lambda^{1/2} \theta_- \leq C \paren{ \int \theta_+ (\del_t\Psi+u\cdot\grad\Psi) + \int \indic{\theta_+>0} }.\]
\end{proof}

With this energy inequality, Proposition~\ref{thm:L2 to Linfty} follows by a standard De Giorgi argument.  Since we will need to make a similar argument again in Section~\ref{sec:de giorgi}, we will write a more general lemma.  

\begin{lemma}[De Giorgi Iteration Argument] \label{thm:DG1 skeleton}
For any constant $\bar{C} > 0$, there exists a $\delta>0$ such that the following holds:

Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  
Let $f \in L^2([-2,0]\times\Omega)$ be a function with the property that for any positive constant $a$
\begin{equation} \label{DG energy ddt} \ddt \int (f-a)_+^2 + \int \abs{\Lambda^{1/2} (f-a)_+}^2 \leq \bar{C} \paren{ \int \indic{f > a} + \int (f-a)_+ + \int (f-a)_+^2 }. \end{equation}

Then
\[ \int_{-2}^0 \int (f-a)_+^2 \,dxdt \leq \delta \]
implies that
\[ f(t,x) \leq 1 \forall t\in[-1,0], x \in \Omega. \]
\end{lemma}

\begin{proof}
Consider for $k \in \N$ the constants $t_k := -1 - 2^{-k}$ (so that $t_0 = -2$ and $t_\infty = -1$), and functions
\[ f_k := (f - 1 + 2^{-k})_+ \]
(so that $f_0 = (f)_+$ and $f_\infty = (f-1)_+$).  

Define
\[ \E_k := \int_{t_k}^0 \int_\Omega f_k^2 \,dxdt. \]

When $f_{k+1}>0$, then in particular $f_k \geq 2^{-k-1}$.  Thus for any finite $p$, there exists a constant $C$ so
\begin{equation} \label{non-linearization} \indic{f_{k+1}>0} \leq C^k f_k^p. \end{equation}
%In particular, 
%\[ \int_\Omega \indic{f_k > 0} + \int_\Omega f_k^2 \leq C^k \int_\Omega \theta_k^3. \]

Let $k\geq 0$, $s \in (t_{k+1},0)$, and let $\eta:[-2,0]\to \R$ be a discontinuous piecewise linear function which vanishes on $[-2,t_k]$, linearly interpolates from 0 to 1 on $[t_k, t_{k+1}]$, is identically 1 on $[t_{k+1}, s]$, and vanishes on $(s,0]$.  Multiplying the inequality \eqref{DG energy ddt} with cutoff $a_k$ by $\eta(t)$ and integrating by parts, we obtain
\[ \int f_k(s,x)^2\,dx - 2^{k+1} \int_{t_k}^{t_{k+1}} \int f_k(t,x)^2 \,dxdt + \int_{t_{k+1}}^s \HDint{1/2}{f_k} \leq C \paren{ \int_{t_k}^0 \int \indic{f_k>0} + f_k + f_k^2 \,dxdt } \]
By taking the supremum over all $s \in (t_{k+1},0)$, we obtain
\begin{equation} \label{DG energy sup}
\sup_{[t_{k+1},0]} \int f_k^2 \,dx + \int_{t_{k+1}}^0 \HDint{1/2}{f_k} \leq C \paren{ 2^{k+1} \int_{t_k}^0 \int f_k^2\,dxdt + \int_{t_k}^0 \int \indic{f_k > 0} + f_k \,dxdt } 
\end{equation}

%\[ \sup_{-1-2^{-k-1}<t<0} \int \theta_{k+1}^2 + \int_{-1-2^{-k-1}}^0 \int \abs{\Lambda^{1/2}\theta_{k+1}}^2 \leq C^k \int_{-1-2^{-k}}^0 \theta_k^2 = \E_k. \]

From Lemma~\ref{thm:hadamard 3 lines} and Sobolev embedding, 
\[ \int_{t_{k+1}}^0 \paren{ \int f_k^4 \,dx }^{1/2} \,dt \leq C \int_{t_{k+1}}^0 \HDint{1/2}{f_k} \,dxdt. \]
Therefore by the Riesz-Thorin interpolation theorem,
\[ \int_{t_{k+1}}^0 \int f_k^3 \,dxdt \leq C \paren{ \sup_{[t_{k+1},0]} \int f_k^2 \,dx + \int_{t_{k+1}}^0 \HDint{1/2}{f_k} }^{3/2}. \]
% However, by Sobolev embedding and the fact that $\HD^{1/2}$ controls classical $H^{1/2}$ controls $L^4$,
This estimate, along with \eqref{DG energy sup} and \eqref{non-linearization}, and the fact that $t_{k-1} < t_k$ and $f_{k-1} \geq f_k$, tell us that
\[ \int_{t_{k+1}}^0 \int f_k^3 \,dxdt \leq C^k \E_{k-1}^{3/2}. \]

Now we can estimate, using again \eqref{non-linearization} and the fact $f_k \geq f_{k+1}$,
\[ \E_{k+1} \leq C^k \int_{t_{k+1}}^0 \int f_k^3 \,dxdt \leq C^k \E_{k-1}^{3/2}. \]

This nonlinear recursive inequality $\E_{k+1} \leq C^k \E_{k-1}^{3/2}$, by a standard fact about nonlinear recursions (see \cite{DG} or \cite{Va.dg}), tells us that for some constant $\delta$ depending only on $C$ (which in turn depends only on the constant $\bar{C}$ in \eqref{DG energy ddt})
\[ \E_0 \leq \delta \implies \lim_{k \to \infty} \E_k = 0. \]

Since
\[ \E_0 = \int_{-2}^0 \int (f)_+ \leq \delta \]
by assumption, we can say $\E_k \to 0$ or, by the dominated convergence theorem,
\[ \int_{-1}^0 \int (f-1)_+ \,dxdt = 0. \]

The result follows.  
\end{proof}


Lemma \ref{thm:L2 to Linfty} is an easy consequence of these lemmas.  

\begin{proof}[Proof of \ref{thm:L2 to Linfty}]
Our regularity assumptions on $\theta$ and $u$ are enough to show, by the usual energy argument, that $\norm{\theta(t,\cdot)}_{L^2(\Omega)}$ is decreasing in time.  By the main result of \cite{CoIg.sqg}, or by applying Lemma~\ref{thm:caccioppoli} with constant cutoff $\Psi(t,x) = \norm{\theta(T,\cdot)}_{L^\infty(\Omega)}$, the $L^\infty$ norm of $\theta(t,\cdot)$ is also decreasing in time once finite.  

In the case $S \geq 1$, $T \geq 2$, we can apply Lemma~\ref{thm:caccioppoli} to establish the family of energy inequalities assumed in Lemma~\ref{thm:DG1 skeleton} and then apply Lemma~\ref{thm:DG1 skeleton} to the function $\frac{\sqrt{\delta}}{\sqrt{2} \norm{\theta_0}_2} \theta$ to show that 
\[ \norm{\theta}_{L^\infty([1,T]\times\Omega)} \leq \paren{\frac{2}{\delta}}^{1/2} \norm{\theta_0}_2. \]

Assuming without loss of generality that $S \leq T/2$, we can apply the above argument to the function $\theta(t/S, x/S)$ to obtain the result for small values of $S$.  
\end{proof}


%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------

\section{Littlewood-Paley Theory} \label{sec:littlewood paley}

In this section we will prove that, because $\theta$ is uniformly bounded in $L^\infty$, the velocity $u = \grad^\perp \Lambda^{-1} \theta$ is calibrated (see Definition~\ref{def:calibrated}).  The proof will utilize a Littlewood-Paley theory adapted to a bounded set $\Omega$.  

Let $\phi$ be a Schwartz function on $\R$ which is suited to Littlewood-Paley decomposition.  Specifically, $\phi$ is non-negative, supported on $[1/2,2]$, and has the property that
\[ \sum_{j \in \Z} \phi(2^j \xi) = 1 \qquad \forall \xi \neq 0. \]
This allows us to define the Littlewood-Paley projections.  For any $f = \sum f_k \eigen{k}$ in $L^2(\Omega)$
\[ P_j f := \sum_k \phi(2^j \lambda_k^{1/2}) f_k \eigen{k}. \]
Note that $P_j$ depends strongly on the domain $\Omega$.  

Recall that $-\Laplace_D$ has some smallest eigenvalue $\lambda_0$ (depending on $\Omega$) so if we define $j_0 = \log_2(\lambda_0)-1$ then $P_j = 0$ for all $j < j_0$.

Our goal in this section is to prove the following proposition:

\begin{proposition} \label{thm:u is calibrated}
Let $\Omega \subseteq \R^2$ be a bounded set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  Let $\theta \in L^\infty(\Omega)$.  Then there exists a sequence of divergence-free functions $(u_j)_{j \in \Z}$ calibrated for some constant $\kappa = \kappa(\Omega, \norm{\theta}_\infty)$ with center 0 (see Definition~\ref{def:calibrated}) such that
\[ \grad^\perp \Lambda^{-1} \theta = \sum_{j \in \Z} u_j \]
with the infinite sum converging in the sense of $L^2$.  

Moreover there exists some $j_0 \in \Z$ such that $u_j = 0$ for all $j < j_0$.  
\end{proposition}

Before we can prove this, we state a few important lemmas.  

The Bernstein Inequalities adapted for a bounded domain are proved in \cite{IMTb}.  We restate their result here:
\begin{lemma}[Bernstein Inequalities] \label{thm:IMT stuff}
Let $1 \leq p \leq \infty$, and $\Omega \subset \R^2$ a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$, and let $(P_j)_{j \in \Z}$ be a Littlewood-Paley decomposition as defined above.  

There exists a constant $C$ depending on $p$ and $\Omega$ such that the following hold for any $f \in L^p(\Omega)$:

For any $\alpha \in \R$ and $j \in \Z$, 
\[ \norm{\Lambda^\alpha P_j f}_{L^p(\Omega)} \leq C 2^{\alpha j} \norm{f}_{L^p(\Omega)}. \]

For any $\alpha \in \R$ and $j \geq j_0$
\[ \norm{\grad \Lambda^\alpha P_j f}_{L^p(\Omega)} \leq C 2^{(1+\alpha) j} \norm{f}_{L^p(\Omega)}. \]
\end{lemma}

\begin{proof}
The first claim is Lemma 3.5 in \cite{IMTb}.  It is also an immediate corollary of \cite{IMTs} Theorem 1.1.  

The second claim is similar to Lemma 3.6 in \cite{IMTb}.  A hypothesis of Lemma 3.6 is that
\[ \norm{\grad e^{-t\Laplace_D}}_{L^\infty \to L^\infty} \leq \frac{C}{\sqrt{t}} \qquad 0 < t \leq 1 \]
(a property of $\Omega$).  The result of Lemma 3.6 only covers the case $j > 0$.  

In \cite{FMP} it is proved that that if $\Omega$ is $C^{2,\alpha}$ then
\[ \norm{\grad e^{-t\Laplace_D}}_{L^\infty \to L^\infty} \leq \frac{C}{\sqrt{t}} \qquad 0 < t \leq T \]
which, by taking some $T$ depending on $j_0$, is enough to prove the desired result for $j \geq j_0$ by a trivial modification of the proof in \cite{IMTb}.  
\end{proof}

The following lemma is a simple but crucial result which can be thought of as describing the commutator of the gradient operator and the projection operators.  In the case of $\R^2$, the Littlewood-Paley projections commute with the gradient so $P_i \grad P_j = 0$ unless $|i-j|\leq 1$.  On a bounded domain, this is not the case.  One can say that the gradient does not maintain localization in frequency-space.  However, the following lemma formalizes the observation that $P_i \grad P_j \approx 0$ when $i << j$.  

\begin{lemma} \label{thm:grad and proj}
There exists a constant $C$ depending on $\Omega$ such that or any function $f \in L^\infty(\Omega)$,
\[ \norm{P_i \grad P_j f}_\infty \leq C \min(2^j,2^i) \norm{f}_\infty. \]
\end{lemma}
\begin{proof}
Let $g$ be an $L^1$ function.  Then since $P_i$ is self-adjoint
\[ \int g P_i \grad P_j f = \int (P_i g) \grad P_j f \leq C 2^j \norm{g}_1 \norm{f}_\infty \]
by Lemma \ref{thm:IMT stuff}.  

Further integrating by parts,
\[ \int g P_i \grad P_j f = - \int (\grad P_i g) P_j f \leq C 2^i \norm{g}_1 \norm{f}_\infty. \]
This also follows from Lemma \ref{thm:IMT stuff}.  

The result follows.  
\end{proof}


This final lemma allows us to interpolate using H\"{o}lder seminorms.  The results are not presumed to be novel, but since their proofs were difficult to find in the literature we include them below.  



We are now ready to prove Proposition \ref{thm:u is calibrated}.  

\begin{proof}
For each $j \in \Z$, we define $u_j$ to be the $\frac{\pi}{2}$-rotation of the Riesz transform of the $j\ith$ Littlewood-Paley projection of $\theta$:
\[ u_j := \grad^\perp \Lambda^{-1} P_j \theta. \]
Qualitatively, we know that $\theta \in L^2$ and hence $u_j \in L^2$.  In fact, $u = \sum u_j$ in the $L^2$ sense.  

We must bound $u_j$, $\Lambda^{-1/4} u_j$, and $\grad u_j$ all in $L^\infty(\Omega)$.  

By straightforward application of Lemma~\ref{thm:IMT stuff},
\begin{equation} \label{uj in Linfty} \norm{u_j}_\infty \leq C \norm{\theta}_\infty. \end{equation}

Since $u_j \in L^2$, we know that
\[ \Lambda^{-1/4} u_j = \sum_{i \in \Z} P_i \Lambda^{-1/4} u_j. \]
Define $\bar{P}_k := P_{k-1} + P_k + P_{k+1}$.  Then $\bar{P}_k P_k = P_k$, and since the projections $P_k$ are spectral operators, they commute with $\Lambda^s$.  We therefore rewrite
\[ \paren{P_i \Lambda^{-1/4} u_j}^\perp = \paren{\Lambda^{-1/4} \bar{P}_i} P_i \grad P_j \paren{\Lambda^{-1} \bar{P}_j} \theta. \]
On the right hand side we have three bounded linear operators applied sequentially to $L^\infty$.  The first operator has norm $C 2^{-j}(2^{1}+2^0+2^{-1})$ by Lemma~\ref{thm:IMT stuff}.  The second operator has norm $C \min(2^j, 2^i)$ by Lemma~\ref{thm:grad and proj}.  The third operator has norm $C 2^{-i/4}(2^{1/4} + 2^0 + 2^{-1/4})$ by Lemma~\ref{thm:IMT stuff}.  (Of course, the perp operator is an isometry.)  Therefore
\[ \norm{ P_i \Lambda^{-1/4} u_j}_\infty \leq C 2^{-i/4} \min(2^j, 2^i) 2^{-j} \norm{\theta}_\infty. \]

Summing these bounds on the projections of $\Lambda^{-1/4} u_j$, and noting that
\[ \sum_{i \in \Z} 2^{-j} 2^{-i/4} \min(2^j,2^i) = 2^{-j} \sum_{i \leq j} 2^{i 3/4} + \sum_{i>j} 2^{-i/4} \leq C 2^{-j/4}, \]
we obtain
\begin{equation}\label{uj in W-1/4} \norm{\Lambda^{-1/4} u_j}_\infty \leq C 2^{-j/4} \norm{\theta}_\infty. \end{equation}

Lastly, we must show that $\grad u_j$ is in $L^\infty$.  Equivalently, we will show that $\Lambda^{-1} P_j \theta$ is $C^{1,1}$.  The method of proof is Schauder theory.  

For convenience, define
\[ F := \Lambda^{-1} P_j \theta. \]
Notice that $F$ is a linear combination of Dirichlet eigenfunctions, so in particular it is smooth and vanishes at the boundary.  Therefore
\[ -\Laplace F = \Lambda^2 F = \Lambda P_j \theta. \]


%For convenience, define 
%\[ F := \Lambda^{-1} P_j \theta \]
%and recall that $F$ is a finite linear combination of Dirichlet eigenfunctions, so in particular it is smooth and vanishes at the boundary.  Moreover, its Laplacian is 
%\[ f := \Laplace F = \Lambda P_j \theta \]
%which is also smooth and vanishes at the boundary.



We apply the standard Schauder estimate from \cite{GiTr} Theorem 6.6 to bound some $C^{2,\alpha}$ semi-norm of $F$ by the $L^\infty$ norm of $F$ and the $C^\alpha$ norm of its Laplacian.  By assumption there exists $\beta \in (0,1)$ such that $\Omega$ is $C^{2,\beta}$, and for this $\beta$ we have by the Schauder estimate
\begin{equation} \label{schauder estimate} \bracket{D^2 F}_{\beta} \leq C \norm{\Lambda^{-1} P_j \theta}_\infty + C \norm{\Lambda P_j \theta}_\infty + C \bracket{\Lambda P_j \theta}_{\beta}. \end{equation}

By Lemma \ref{thm:IMT stuff},
\begin{align*} 
\norm{\Lambda^{-1} P_j \theta}_\infty &\leq C 2^{-j} \norm{\theta}_\infty, \\
\norm{\Lambda P_j \theta}_\infty &\leq C 2^j \norm{\theta}_\infty, \\
\norm{\grad \Lambda P_j \theta}_\infty &\leq C 2^{2j} \norm{\theta}_\infty. 
\end{align*}
%\begin{align*} 
%\norm{F}_\infty &= \norm{\Lambda^{-1} P_j \theta}_\infty \leq C 2^{-j} \norm{\theta}_\infty, \\
%\norm{f}_\infty &= \norm{\Lambda P_j \theta}_\infty \leq C 2^j \norm{\theta}_\infty, \\
%\norm{\grad f}_\infty &= \norm{\grad \Lambda P_j \theta}_\infty \leq C 2^{2j} \norm{\theta}_\infty. 
%\end{align*}
By Lemma~\ref{thm:interpolation C1 to holder} (see Appendix~\ref{sec:technical}) we can interpolate these last two bounds to obtain
\[ \bracket{\Lambda P_j \theta}_\beta \leq C 2^{j(1+\beta)} \norm{\theta}_\infty. \]
Plugging these estimates into \eqref{schauder estimate} yields
\[ \bracket{D^2 F}_\beta \leq C \paren{2^{-j} + 2^j + 2^{j(1+\beta)}} \norm{\theta}_\infty. \]

Recall that without loss of generality we can assume $j \geq j_0$.  Therefore up to a constant depending on $j_0$, the term $2^{j(1+\beta)}$ bounds $2^j$ and $2^{-j}$ so we can write
\[ \bracket{D^2 F}_\alpha \leq C 2^{j(1+\beta)} \norm{\theta}_\infty. \]

Using this estimate and the fact that $\norm{\grad F}_\infty = \norm{\grad \Lambda^{-1} P_j \theta}_\infty \leq C \norm{\theta}_\infty$ (see \eqref{uj in Linfty}), we can interpolate to obtain an $L^\infty$ bound on $D^2 F$.  
Lemma~\ref{thm:interpolation holder to C1} states that since $F \in C^{2,\beta}$ and $\Omega$ is sufficiently regular, there exist a constant $\ell = \ell(\Omega)$ such that for any $\delta \in [0, \ell]$ we have
\begin{align*}
\norm{D^2 F}_\infty &\leq C \paren{\delta\n \norm{\grad F}_\infty + \delta^{\beta} \bracket{D^2 F}_\beta}
\\ &\leq C \paren{\delta\n + \delta^\beta 2^{j(1+\beta)}} \norm{\theta}_\infty.  
\end{align*}

Set $\delta = 2^{-j} (2^{j_0} \ell) \leq \ell$.  Then
\[ \norm{D^2 F}_\infty \leq C \paren{C 2^j + 2^{-j\beta} 2^{j(1+\beta)}} \norm{\theta}_\infty = C(\Omega) 2^j \norm{\theta}_\infty. \]

Since $D^2 F = \grad u_j$, this estimate together with \eqref{uj in Linfty} and \eqref{uj in W-1/4} complete the proof.  
\end{proof}


%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------

\section{De Giorgi Estimates} \label{sec:de giorgi}

Our goal in this section is to prove De Giorgi's first and second lemmas for solutions to \eqref{eq:main linear} with $u$ uniformly calibrated.  

The first step is to show that a calibrated velocity can be rewritten in a more practical format:
\begin{lemma} \label{thm:calibration is good}
Let 
\[ u = \sum_{j_0}^\infty u_j \]
with the sum converging in the $L^2$ sense.  Assume that $(u_j)_{j \in \Z}$ is a calibrated sequence with constant $\kappa$ and some center, and that $\div(u_j)=0$.  

Then
\[ u = \ulow + \uhigh \]
with 
\begin{align*} 
\norm{\grad \ulow}_{L^\infty([-T,0]\times \Omega)} &\leq 2 \kappa, \\
\norm{\Lambda^{-1/4} \uhigh}_{L^\infty([-T,0]\times\Omega)} &\leq 6 \kappa. 
\end{align*}
and $\div(\ulow) = \div(\uhigh) = 0$.  
\end{lemma}

We call $\ulow$ the low-pass term, and $\uhigh$ the high-pass term.  

\begin{proof}
Let $N$ be the center to which $(u_j)_{j \in \Z}$ is calibrated.  

We define
\[ \uhigh = \sum_{j > N} u_j \]
and bound
\[ \norm{\Lambda^{-1/4} \uhigh}_\infty \leq \sum_{j>N} \norm{\Lambda^{-1/4} u_j}_\infty \leq \kappa \frac{2^{-1/4}}{1-2^{-1/4}}. \]

We define
\[ \ulow = \sum_{j = j_0}^N u_j. \]
and bound
\[ \norm{\grad \ulow}_\infty \leq \sum_{j \leq N} \norm{\grad u_j}_\infty \leq \kappa \frac{1}{1 - 2^{-1}}. \]
\end{proof}

In order to prove the De Giorgi lemmas, we must derive an energy inequality for the function $\paren{\theta - \Psi}_+$ where $\Psi(t,x)$ is not constant, but rather grows sublinearly in $|x|$.  However, applying Lemma~\ref{thm:caccioppoli} to such a function, we see that its derivatives are only small if the quantity $\del_t \Psi + u \cdot \grad\Psi$ is bounded.  

To that end, we shall consider a family of functions $\theta$, $\ulow$, and $\uhigh:[-T,0]\times \Omega \to \R$, and paths $\Gamma$ and $\gamma:[-5,0] \to \R^2$ which satisfy
\begin{equation} \label{eq:main linear brokendown} \begin{cases}
\del_t \theta + (\ulow + \uhigh) \cdot \grad \theta + \Lambda \theta = 0 & \textrm{on } [-T,0] \times \Omega, \\
\div( \ulow) = \div(\uhigh) = 0 & \textrm{on } [-T,0]\times \Omega, \\
\dot{\Gamma}(t) + \dot{\gamma}(t) = \ulow(t, \gamma(t) + \Gamma(t)) & \textrm{on } [-T,0], \\
\gamma(0) = \Gamma(0) = 0.
\end{cases} \end{equation}

Here it is implicitly assumed that $\gamma(t) + \Gamma(t) \in \Omega$.  Generally speaking $\ulow$ and $\gamma$ will be locally Lipschitz functions while $\uhigh$ is merely in a weak space $W^{-1/4,\infty}$ and $\Gamma$ will trace out points in $\Omega$ where $\theta$ is well behaved by assumption.  See Section~\ref{sec:holder} for the construction of these functions $\Gamma$ and $\gamma$.  

Now we prove an energy inequality for solutions to \eqref{eq:main linear brokendown}.  

\begin{lemma}[Energy inequality] \label{thm:energy inequality}
Let $\kappa$, $\Comega$, $\Cgamma$, $T$, and $R$ be positive constants, and let $\psi:\R^2 \to \R$ be a function with bounded first and second derivatives. Then there exists a constant $C>0$ such that the following holds:

Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  Assume that Lemma~\ref{thm:Caff Stinga representation} hold on $\Omega$ with kernels that satisfy
\[ K_{1/4}(x,y) \leq \Comega |x-y|^{1/2} K_{1}. \]

Let $\theta$, $\ulow$, $\uhigh$, $\Gamma$ and $\gamma$ solve \eqref{eq:main linear brokendown} on $[-T,0]\times\Omega$, and satisfy $\norm{\Lambda^{-1/4} \uhigh}_{L^\infty([-T,0]\times\Omega)} \leq 6 \kappa$, $\norm{\grad \ulow}_{L^\infty([-T,0]\times\Omega)} \leq 2\kappa$, and $\norm{\dot{\gamma}}_{L^\infty([-T,0])} \leq \Cgamma$.  

Let $\psi:\R^2 \to \R$ have bounded derivative and bounded second derivative, and consider the functions
\[ \theta_+ := \paren{\theta - \psi(\cdot-\Gamma)}_+, \qquad \theta_- := \paren{\psi(\cdot-\Gamma) - \theta}_+. \]

If $\theta_+$ is supported on $x \in \Omega \cap B_R(\Gamma(t))$ for some $R>0$, then $\theta_+$ and $\theta_-$ satisfy the inequality
\[ \ddt \int \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2 - \chevron{\theta_+,\theta_-}_{1/2} \leq C \paren{ \int \indic{\theta_+ > 0} + \int \theta_+ + \int \theta_+^2 }. \]
%with the constant $C$ depending on $\Cgamma$ and $T$, on $\norm{\Lambda^{-1/4} \uhigh}_\infty$, $\bracket{\ulow}_{3/4}$, and $\norm{\ulow}_\Lip$, and on $\norm{D^2 \phi}_\infty$, $\norm{\grad\phi}_\infty$, and $\sup \norm{|x|^{3/4} \grad\phi(x)}_\infty$.  
\end{lemma}

\begin{proof}
Define 
\[ \Psi(t,x) := \psi(x - \Gamma(t)) \]
so that
\[ \del_t \Psi + (\ulow + \uhigh)\cdot\grad \Psi = (\ulow - \dot{\Gamma} + \uhigh)\cdot \grad \psi(x-\Gamma(t)). \]

Applying Lemma \ref{thm:caccioppoli} to $\theta$ and $\Psi$ we arrive at
\[ \ddt \int \theta_+^2 + \int \abs{\Lambda^{1/2} \theta_+}^2 - \chevron{\theta_+,\theta_-}_{1/2} \leq C \paren{ \int \indic{\theta_+ > 0} + \int \theta_+ (\ulow-\dot{\Gamma}(t) + \uhigh) \cdot \grad\psi(x-\Gamma(t)) }. \]

Consider first the high-pass term $\int \theta_+ \uhigh\cdot\grad\psi$.  By inserting $\Lambda^{1/4}\Lambda^{-1/4}$ and then integrating by parts, we can apply Lemma~\ref{thm:Lambda stuff} parts \eqref{thm:L1 of Lambda1/4 bounded} and \eqref{thm:extra product rule} to obtain
\[ \int \Lambda^{-1/4} \uhigh \Lambda^{1/4} (\theta_+ \grad\psi) \leq C \norm{\Lambda^{-1/4} \uhigh}_\infty \paren{\norm{\grad\psi}_\infty + \norm{D^2 \psi}_\infty} |\supp(\theta_+)|^{1/2} \paren{ \norm{\theta_+}_{L^2} + \norm{\theta_+}_{\HD^{1/2}}}. \]
From H\"{o}lder's inequality with Peter-Paul, we obtain
%\[ \int \Lambda^{-1/4} \uhigh \Lambda^{1/4} (\theta_+ \grad\psi) \leq C(\phi,\eps) \norm{\Lambda^{1/4} \uhigh}_\infty \paren{\int \theta_+ + |\{\theta_+>0\}| + \int \theta_+^2 + \eps\n |\{\theta_+ > 0\}| + \eps \int \abs{\Lambda^{1/2} \theta_+}^2 }. \]
\[ \int \uhigh \theta_+ \grad \psi(x - \gamma(t)) \,dx \leq C(\psi,\eps) \kappa \paren{\int \indic{\theta_+>0} + \int \theta_+^2} + \eps \int \abs{\Lambda^{1/2} \theta_+}^2. \]

Consider now the low-pass term.  Recall that
\[ \dot{\Gamma} + \dot{\gamma} = \ulow(t, \Gamma+\gamma) \]
so
\begin{equation} \label{low pass term definition} \ulow(t,x) - \dot{\Gamma}(t) = \ulow(t,x) - \ulow(t,\Gamma+\gamma) + \dot{\gamma}. \end{equation}

By assumption, $|\dot{\gamma}|\leq \Cgamma$ and so for $t \in [-T,0]$ we have $|\gamma(t)| \leq T \Cgamma$.  

Since $\ulow$ is has bounded derivative,
\begin{align*} 
|\ulow(t,x) - \ulow(t,\Gamma+\gamma)| &\leq  |\ulow(t,x)-\ulow(t,\Gamma)| + |\ulow(t,\Gamma) - \ulow(t,\Gamma+\gamma)| 
\\ &\leq 2\kappa |x-\Gamma| + 2\kappa T \Cgamma. 
\end{align*}

Plugging these bounds into \eqref{low pass term definition} we obtain
\[ \abs{\ulow(t,x) - \dot{\Gamma}(t)} \leq (1+2\kappa T) \Cgamma + 2\kappa |x-\Gamma|. \]

Now we can bound the low pass term
%\begin{align*}
\[ \int (\ulow - \dot{\Gamma}) \theta_+ \grad\psi(x-\Gamma) \leq (1+2\kappa T) \Cgamma \norm{\grad\psi}_\infty \int \theta_+ \,dx +  \norm{\grad\psi}_\infty 2\kappa \int |x-\Gamma| \theta_+ \,dx. \]
%\\ &\leq (1+\norm{\grad\ulow}_\infty T) \Cgamma \norm{\grad\psi}_\infty \int \theta_+ \,dx +  \bracket{\ulow}_{3/4} \norm{|x|^{3/4} \grad\psi(x)}_\infty \int \theta_+ \,dx.
%\end{align*}
By assumption, $|x-\Gamma| \theta_+ \leq R \theta_+$, so the result follows.  
\end{proof}

This energy inequality is sufficient to apply the method of De Giorgi.  

\begin{proposition}[First De Giorgi Lemma] \label{thm:DG1}

Let $\kappa$, $\Comega$, and $\Cgamma$, be positive constants. Then there exists a constant $\delta_0>0$ such that the following holds:

Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  Assume that Lemma~\ref{thm:Caff Stinga representation} hold on $\Omega$ with kernels that satisfy
\[ K_{1/4}(x,y) \leq \Comega |x-y|^{1/2} K_{1}. \]

Let $\theta$, $\ulow$, $\uhigh$, $\Gamma$ and $\gamma$ solve \eqref{eq:main linear brokendown} on $[-2,0]\times\Omega$, and satisfy $\norm{\Lambda^{-1/4} \uhigh}_{L^\infty([-2,0]\times\Omega)} \leq 6 \kappa$, $\norm{\grad \ulow}_{L^\infty([-2,0]\times\Omega)} \leq 2\kappa$, and $\norm{\dot{\gamma}}_{L^\infty([-2,0])} \leq \Cgamma$.  

If
\[ \theta(t,x) \leq 2 + \paren{|x-\Gamma(t)|^{1/4}-2^{1/4}}_+ \qquad \forall t\in[-2,0], x \in \Omega \setminus B_2(\Gamma(t)) \]
and
\[ \int_{-2}^0 \int_{\Omega\cap B_2(\Gamma(t))} (\theta)_+^2 \,dxdt \leq \delta_0 \]
then
\[ \theta(t,x) \leq 1 \qquad \forall t \in [-1,0], x \in \Omega \cap B_1(\Gamma(t)). \]

\end{proposition}

\begin{proof}
Let $\psi$ be such that $\psi = 0$ for $|x| \leq 1$ and $\psi(x) \geq 2 + \paren{|x|^{1/4}-2^{1/4}}_+$ for $|x|>2$, and let $\grad \psi$ and $D^2 \psi$ be bounded.  

For any constant $a > 0$, we can apply Lemma~\ref{thm:energy inequality} to the function
\[ \theta_a := (\theta(t,x) - \psi(x - \Gamma(t)) - a)_+ \]
and obtain
\[ \ddt \int \theta_a^2 + \int \abs{\Lambda^{1/2} \theta_a}^2 \leq C \paren{ \int \indic{\theta_a > 0} + \int \theta_a + \int \theta_a^2 }. \]

Thus $\theta - \psi(x-\Gamma)$ satisfies the assumptions of Lemma~\ref{thm:DG1 skeleton}.  There exists a constant, which we call $\delta_0$, so that if
\[ \int_{-2}^0 \int \paren{\theta(t,x) - \psi(x-\Gamma(t))}_+ \,dxdt \leq \delta_0 \]
then 
\[ \theta(t,x) \leq 1 + \psi(x-\Gamma(t)) \qquad \forall t \in [-1,0], x \in \Omega. \]

By construction of $\psi$, our result follows immediately.  

\end{proof}

Next, we will prove De Giorgi's second lemma, a quantitative analog of the isoperimetric inequality.  

\begin{lemma}[Second De Giorgi Lemma] \label{thm:DG2}
Let $\kappa$, $\Comega$, and $\Cgamma$, be positive constants. Then there exists a constant $\mu>0$ such that the following holds:

Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  Assume that Lemma~\ref{thm:Caff Stinga representation} hold on $\Omega$ with kernels that satisfy
\[ K_{1/4}(x,y) \leq \Comega |x-y|^{1/2} K_{1}. \]

Let $\theta$, $\ulow$, $\uhigh$, $\Gamma$ and $\gamma$ solve \eqref{eq:main linear brokendown} on $[-2,0]\times\Omega$, and satisfy $\norm{\Lambda^{-1/4} \uhigh}_{L^\infty([-2,0]\times\Omega)} \leq 6 \kappa$, $\norm{\grad \ulow}_{L^\infty([-2,0]\times\Omega)} \leq 2\kappa$, and $\norm{\dot{\gamma}}_{L^\infty([-2,0])} \leq \Cgamma$.  

Suppose that for $t \in [-5,0]$ and any $x \in \Omega$,
\[ \theta(t,x) \leq 2 + \paren{|x-\Gamma(t)|^{1/4}-2^{1/4}}_+. \]

Then the three conditions
\begin{align} 
\abs{\{\theta \geq 1\} \cap [-2,0]\times B_2(\Gamma)} &\geq \delta_0/4, \label{mass assumption above} \\
\abs{\{0 < \theta < 1\} \cap [-4,0]\times B_4(\Gamma)} &\leq \mu, \nonumber \\
\abs{\{\theta \leq 0\} \cap [-4,0]\times B_4(\Gamma)} &\geq 2 |B_4| \label{mass assumption below}
\end{align}
cannot simultaneously be met.  
\end{lemma}

Here $\delta_0$ is the constant from Lemma~\ref{thm:DG1}, which of course depends on $\kappa$, $\Cgamma$, and $\Comega$.  

\begin{proof}
Suppose that the theorem is false.  Then there must exist, for each $n \in \N$, a bounded $C^{2,\alpha}$ set $\Omega_n$ and function $\theta_n: [-5,0]\times \Omega_n \to \R$, functions $\ulow^n, \uhigh^n: [-5,0]\times\Omega_n \to \R^2$, and paths $\Gamma_n,\gamma_n:[-5,0]\to\R^2$ which solve \eqref{eq:main linear brokendown} and satisfy all of the the assumptions of our lemma (with the same constants $\kappa$, $\Cgamma$, and $\Comega$), except that
\begin{equation} \label{mass assumption between} \abs{\{0 < \theta_n < 1\} \cap [-4,0]\times B_4(\Gamma_n)} \leq 1/n. \end{equation}

Let $\psi:\R^2 \to \R$ be a smooth function which vanishes on $B_2$ such that $\psi(x) = 2 + \paren{|x|^{1/4}-2^{1/4}}_+$ for $|x|>3$.  

Fix $n$ and define 
\[ \theta_+ := \paren{\theta_n - \psi(x-\Gamma_n)}_+. \]
Then $\theta_+$ is supported on $\Omega \cap B_3(\Gamma_n)$ and is less than $2 + 3^{1/4} - 2^{1/4} \leq 3$ everywhere.  

Our goal is to bound the derivatives of $\theta_+^3$ so that we can apply a compactness argument to the sequence $\theta_n$.  (For the curious reader, we will point out the steps below in which it is important to consider $\theta_+^3$ instead of $\theta_+$.)  

Apply the energy inequality Lemma \ref{thm:energy inequality} to $\theta$ and $\psi(x-\Gamma_n)$, and find that for some $C$ independent of $n$
\begin{equation} \label{ddt theta bounded} \ddt \int \theta_+^2 \leq C \end{equation}
and moreover that
\begin{equation}\label{DG2 energy} \sup_{[-4,0]} \int \theta_+^2 + \int_{-4}^0 \int \abs{\Lambda^{1/2}\theta_+}^2 + \int_{-4}^0 \int \Lambda^{1/2}\theta_+ \Lambda^{1/2}\theta_- \leq C. \end{equation}
This proves in particular that $\theta_+ \in L^2(-4,0; \HD^{1/2}(\Omega))$ is uniformly bounded.  

What's more, $\norm{\theta_+^3}_{L^2(-4,0;\HD^{1/2}(\Omega_n))}$ is uniformly bounded because
\begin{align*} 
\norm{\Lambda^{1/2}(\theta_+^3)}_2^2 &= \iint [\theta_+(x)^3 - \theta_+(y)^3]^2 K + \int \theta_+^6 B 
\\ &\leq 2\iint \theta_+(x)^4 [\theta_+(x)-\theta_+(y)]^2 K + 2\iint \theta_+(y)^4[\theta_+(x)-\theta_+(y)]^2 K + \norm{\theta_+}_\infty^4 \int \theta_+^2 B
\\ &\leq C \norm{\theta_+}_\infty^4 \norm{\theta_+}_{\HD^{1/2}}^2.  
\end{align*}

By Lemma \ref{thm:hadamard 3 lines}, if $E \theta_+^3$ is the zero-extension of $\theta_+^3$ from $\Omega_n$ to $\R^2$, then
\begin{equation} \label{theta3 compact in space} \norm{ E \theta_+^3}_{L^2(-4,0; H^{1/2}(\R^2))} \leq C \end{equation}
where $C$ does not depend on $n$.  

Since $\theta_n$ solves the equation
\[ \del_t \theta_n + (\uhigh + \ulow)\cdot \grad \theta_n + \Lambda \theta_n = 0, \] 
multiply this equation by $\varphi \theta_+^2$, where $\varphi$ is any function in $C^2(\R^2)$ restricted to $\Omega_n$, and integrate to obtain
\begin{align*} 
\frac{1}{3} \int \varphi \del_t \theta_+^3 + \frac{1}{3} \int \varphi \dot{\Gamma}_n \cdot \grad \theta_+^3 &= \frac{-1}{3} \int \varphi (\ulow^n - \dot{\Gamma}_n + \uhigh^n) \cdot \grad \theta_+^3 - \int \varphi \theta_+^2 (\ulow^n - \dot{\Gamma}_n + \uhigh^n) \cdot \grad \psi 
\\ & - \int \varphi \theta_+^2 \Lambda \theta_+ - \int \varphi \theta_+^2 \Lambda \psi + \int \varphi \theta_+^2 \Lambda \theta_-. 
\end{align*}
Further rearranging, this becomes
\begin{align*} 
\int \varphi \del_t \theta_+^3 + \int \varphi \dot{\Gamma}_n \cdot \grad \theta_+^3 
&= \int (\ulow^n - \dot{\Gamma}_n) \cdot (\theta_+^3 \grad\varphi - 3 \varphi \theta_+^2 \grad\psi) + \int \Lambda^{-1/4} \uhigh^n \Lambda^{1/4} \paren{\theta_+^3 \grad\varphi - 3 \varphi \theta_+^2 \grad\psi}
\\ & - 3\int \varphi \theta_+^2 \Lambda \theta_+ - 3\int \varphi \theta_+^2 \Lambda \psi + 3\int \varphi \theta_+^2 \Lambda \theta_-. 
\end{align*}
We will bound the five terms on the right hand side one at a time.  

Each instance of $C$ in the following bounds is independent of $n$.  

\begin{itemize}
\item Consider the low-pass term.  As in the proof of Lemma~\ref{thm:energy inequality}, we have $|\ulow^n(t,x) - \dot{\Gamma}_n(t)| \leq (1+8\kappa)\Cgamma + 6 \kappa$ for $t \in [-4,0]$ and $x \in \supp(\theta_+) \subseteq \Omega_n \cap B_3(\Gamma_n(t))$.  Thus for $t \in [-4,0]$ we have for $C$ independent of $n$ and of $\varphi$
\[ \int (\ulow^n - \dot{\Gamma}_n) \cdot (\theta_+^3 \grad\varphi - 3 \varphi \theta_+^2 \grad\psi) \leq C \paren{\norm{\grad\varphi(t,\cdot)}_{L^\infty(\Omega)} + \norm{\varphi(t,\cdot)}_{L^\infty(\Omega)}}. \]

\item Consider the high-pass term.  By Lemma \ref{thm:Lambda stuff} parts \ref{thm:L1 of Lambda1/4 bounded} and \ref{thm:extra product rule}, 
\[ \int \Lambda^{-1/4} \uhigh^n \Lambda^{1/4} \paren{\theta_+^3 \grad\varphi - 3 \varphi \theta_+^2 \grad\psi} \leq C \kappa |\supp(\theta_+)|^{1/2} \paren{\norm{\theta_+^3 \grad\varphi}_{L^2} + \norm{\varphi \theta_+^2 \grad\psi}_{L^2} + \norm{\theta_+^3 \grad\varphi}_{\HD^{1/2}} + \norm{\varphi \theta_+^2 \grad\psi}_{\HD^{1/2}}}. \]
\[ \leq C \paren{ \norm{\varphi(t,\cdot)}_{C^1(\Omega)} + \norm{\varphi(t,\cdot)}_{C^2(\Omega)} \norm{\theta(t,\cdot)}_{\HD^{1/2}} }. \]

\item Consider the $\Lambda \theta_+$ term.  Decomposing this term using Proposition~\ref{thm:Caff Stinga representation} we have first an interior term $\iint [\varphi(x)\theta_+(x)^2 - \varphi(y)\theta_+(y)^2][\theta_+(x)-\theta_+(y)] K$ which decomposes as
\[ \iint \varphi(x)(\theta_+(x)+\theta_+(y))[\theta_+(x)-\theta_+(y)]^2 K + \iint \theta_+(y)^2 [\varphi(x)-\varphi(y)][\theta_+(x)-\theta_+(y)] K. \]
The first part is bounded by the $L^\infty$ norms of $\varphi$ and $\theta_+$ and the square of the $\HD^{1/2}$ norm of $\theta_+$, while the second part is bounded
\[ \iint \theta_+(y)^2 [\varphi(x)-\varphi(y)][\theta_+(x)-\theta_+(y)] K \leq \norm{\theta_+(t,\cdot)}_{\HD^{1/2}} \sqrt{\int \theta_+(y)^2 \int \frac{[\varphi(x)-\varphi(y)]^2}{|x-y|^3} dx \,dy}\]
which is bounded by the $C^1$ norm of $\varphi$ and the $\HD^{1/2}$ norm of $\theta_+$.  
% (using H\"{o}lder's inequality) by the $L^\infty$ and $\HD^{1/2}$ norms of $\theta_+$ and the square root of $\sup_y \int [\varphi(x)-\varphi(y)]^2/|x-y|^3 \,dx$.  This last quantity is in turn bounded by the $C^1$ norm of $\varphi$.  

The boundary term $\int \varphi \theta_+^3 B$ is bounded by the $L^\infty$ norms of $\varphi$ and $\theta_+$, and by $\int \theta_+^2 B$ which is less than $\norm{\theta_+(t,\cdot)}_{\HD^{1/2}}$.  Taken together we have
\[ \int \varphi \theta_+^2 \Lambda \theta_+ \leq C \paren{ \norm{\varphi(t,\cdot)}_{L^\infty(\Omega)} \norm{\theta_+(t,\cdot)}_{\HD^{1/2}}^2 + \norm{\varphi(t,\cdot)}_{C^1(\Omega)} \norm{\theta_+(t,\cdot)}_{\HD^{1/2}} }. \]

\item Consider the $\Lambda\theta_-$ term.  For any non-negative function $f$ we know by Lemma~\ref{thm:Lambda stuff} part \eqref{thm:disjoint} that $\int f \theta_+ \Lambda \theta_- \leq 0$.  
It follows that $-\theta_+ \Lambda \theta_-$ is a pointwise non-negative distribution.  Moreover, the integral over $[-4,0]\times\Omega$ of $-\theta_+\Lambda\theta_-$ is bounded by \eqref{DG2 energy}.  Thus $\theta_+\Lambda\theta_-$ is a measure with bounded total-variation norm.  In fact, because $\varphi$ is a continuous function,
\[ \int_{-4}^0 \int \varphi \theta_+^2 \Lambda \theta \leq \norm{\theta_+}_\infty \norm{\theta_+\Lambda\theta_-}_{\mathcal{M}} \norm{\varphi}_{C^0} \leq C \norm{\varphi}_{L^\infty([-4,0]\times\Omega)}. \]

\item Consider the $\Lambda \psi$ term.  Decomposing this term using Proposition~\ref{thm:Caff Stinga representation} we have first an interior term $\iint [\varphi(x) \theta_+(x)^2 - \varphi(y) \theta_+(y)^2][\psi(x)-\psi(y)] K$ which decomposes as
\[ \int \theta_+(y)^2\int[\varphi(x) - \varphi(y)][\psi(x)-\psi(y)] K + \iint \varphi(x) [\theta_+(x)^2 - \theta_+(y)^2][\psi(x)-\psi(y)] K. \]
The first part is bounded by the $C^1$ norms of $\varphi$ and $\psi$ and the $L^2$ norm of $\theta_+$, while the second part is bounded
\[ \iint \varphi(x) [\theta_+(x)^2 - \theta_+(y)^2][\psi(x)-\psi(y)] K \leq \norm{\theta_+^2(t,\cdot)}_{\HD^{1/2}} \sqrt{ \int \varphi(x)^2 \int \frac{[\psi(x)-\psi(y)]^2}{|x-y|^3}dy \,dx} \]
which is bounded, because $\psi$ is smooth and globally $1/4$-H\"{o}lder continuous, by $L^2$ norm of $\varphi$ and the $\HD^{1/2}$ norm of $\theta_+$.  

The boundary term $\int \varphi \theta_+^2 \psi B$ is bounded by the $L^\infty$ norms of $\varphi$ and $\psi \indic{\theta_+>0}$ and by $\int \theta_+^2 B$ which is less than $\norm{\theta_+(t,\cdot)}_{\HD^{1/2}}^2$.  Taken together we have
\[ \int \varphi \theta_+^2 \Lambda \psi \leq C \paren{ \norm{\varphi(t,\cdot)}_{C^1(\Omega)} + \norm{\varphi(t,\cdot)}_{L^2(\Omega)} \norm{\theta_+(t,\cdot)}_{\HD^{1/2}} + \norm{\varphi(t,\cdot)}_{L^\infty(\Omega)} \norm{\theta_+(t,\cdot)}_{\HD^{1/2}}^2 }. \]
%
% Lastly, 
%\begin{align*} 
%\int \varphi \theta_+^2 \Lambda \psi &= \iint [\varphi(x) \theta_+(x)^2 - \varphi(y) \theta_+(y)^2][\psi(x)-\psi(y)] K + \int \varphi \theta_+^2 \psi B
%\\ &= \iint \varphi(x) [\theta_+(x)^2 - \theta_+(y)^2][\psi(x)-\psi(y)] K + \iint \theta_+(y)^2[\varphi(x) - \varphi(y)][\psi(x)-\psi(y)] K + \int \varphi \theta_+^2 \psi B
%\\ &\leq C\paren{\iint \varphi(x)^2 [\psi(x)-\psi(y)]^2 K}^{1/2} + \paren{ \norm{\varphi}_\infty + \norm{\grad \varphi}_\infty } \int \theta_+(y)^2 \,dy + \int \varphi \theta_+^2 \psi B
%\\ &\leq C \norm{\varphi}_{L^2} + C \norm{\varphi}_{\infty} + C \norm{\grad \varphi}_\infty + \norm{\psi\indic{\theta_+>0}}_\infty \norm{\theta_+}_{\HD^{1/2}}^2 \norm{\varphi}_{\infty}
%\\ &= C \norm{\psi}_{L^\infty(-4,0; L^2(\Omega_n))} + C \norm{\varphi}_{L^\infty(-4,0; L^\infty(\Omega_n))} + C \norm{\grad\varphi}_{L^\infty(-4,0; L^\infty(\Omega_n))}.
%\end{align*}

\end{itemize}

\begin{remark}
We are attempting to bound $\del_t \theta_+^3$.  If we had attempted to bound $\del_t \theta_+^p$ instead, the final three terms above would have been problematic for $p=1$ and the very final term would have been problematic for $p=2$.  
\end{remark}

Combining all of these bounds, and using the fact that $\theta_+ \in L^2(-4,0; \HD^{1/2})$ uniformly, we conclude that there exists a constant $C$ independent of $n$ such that, for any $\varphi \in L^\infty(-4,0; C^2(\R^2)) \cap L^\infty(-4,0; L^2(\R^2))$, 
\begin{equation} \label{theta3 compact in time} \int_{-4}^0 \int_{\Omega_n} \paren{ \del_t \theta_+^3 + \dot{\Gamma}_n \cdot \grad \theta_+^3 } \varphi \,dxdt \leq C \norm{\varphi}_{L^\infty(-4,0; C^2(\R^2))} + C \norm{\varphi}_{L^\infty(-4,0; L^2(\R^2))}. \end{equation}

Over time, the support of $\theta_+^3$ moves around in $\Omega_n$ following the path $\Gamma_n$.  In order to take a meaningful limit in $n$, we must shift these functions so that their supports remain in a compact set.  To that end, define a new function on $[-4,0] \times \R^2$ by
\[ v_n(t,x) := \begin{cases}
\theta_+(t, x + \Gamma_n(t))^3, & x + \Gamma_n(t) \in \Omega_n, \\
0, & x + \Gamma_n(t) \notin \Omega_n.
\end{cases} \]
In other words,
\begin{equation} \label{definition of v_n} v_n(t,x) = \paren{\theta_n(t, x + \Gamma_n(t)) - \psi(x)}_+^3 \end{equation}
when the right hand side is defined.

Let $X \subseteq C^2(\R^2)$ be the Banach space of $C^2$ functions with norm $\norm{\cdot}_X = \norm{\cdot}_{C^2(\R^2)} + \norm{\cdot}_{L^2(\R^2)}$ finite.  Note that
\[ \del_t v_n(t,x) = \del_t \theta_+^3(t,x+\Gamma_n) + \dot{\Gamma}_n \cdot \grad \theta_+^3(t,x+\Gamma_n). \]

We know from \eqref{theta3 compact in space} that
\[ \norm{ v_n }_{L^2(-4,0; H^{1/2}(\R^2)} \leq C \]
and from \eqref{theta3 compact in time} that
\[ \norm{ \del_t v_n }_{L^1(-4,0; X^*)} \leq C. \]

According to the Aubin-Lions Lemma, the set $\{v_n\}_n$ is therefore compactly embedded in $L^2([-4,0]\times\R^2)$.  Up to a subsequence, there is a function $v \in L^2([-4,0]\times\R^2)$ such that
\[ v_n \to v. \]
By elementary properties of $L^2$ convergence, we know that $v \in L^\infty$, $\supp(v) \subseteq [-4,0]\times B_3(0)$, and $v \in L^2(H^{1/2})$.  

By \eqref{ddt theta bounded}
\begin{equation} \label{ddt v bounded} \ddt \int_{\R^2} v_n^{2/3} \,dx = \ddt \int_{\Omega_n} \theta_+^2 \,dx \leq C \end{equation}
so the same must be true of $v$.

By \eqref{mass assumption above}, \eqref{mass assumption between}, and \eqref{mass assumption below} applied to $v_n$ (recalling the relation \eqref{definition of v_n}), we conclude that
\begin{equation} \label{mass assumptions v} \begin{cases} 
\abs{\{v \geq 1\} \cap [-2,0]\times B_2(0)} &\geq \delta_0/4, \\
\abs{\{0 < v < [1-\psi]^3\} \cap [-4,0]\times B_4(0)} &\leq 0, \\
\abs{\{v \leq 0\} \cap [-4,0]\times B_4(0)} &\geq 2|B_4|
\end{cases} \end{equation}

%\begin{align} 
%\abs{\{v_n \geq 1\} \cap [-2,0]\times B_2(0)} &\geq \delta_0, \\
%\abs{\{0 < v_n < [1-\psi(x)]^3\} \cap [-4,0]\times B_4(0)} &\leq 1/n, \\
%\abs{\{v_n \leq 0\} \cap [-4,0]\times B_4(0)} &\geq 2|B_4|
%\end{align}

For any $(t,x) \in [-4,0]\times B_4(0)$, either $v(t,x) \geq [1 - \psi(x)]^3$ or else $v(t,x) = 0$.  In fact, since $\norm{v(t,\cdot)}_{H^{1/2}} < \infty$ for almost every $t$ and $H^{1/2}$ does not contain functions with jump discontinuities, the function $v$ is either identically 0 or else $\geq [1-\psi(x)]^3$ at each $t$.  

Thus $\int v(t,x)^{2/3} \,dx$ is either 0 or else $\geq \int [1-\psi(x)]^3 \,dx > 0$ at each $t$.  By \eqref{ddt v bounded} and \eqref{mass assumptions v}, $v$ must be identically zero for all $t > -2$ but also must be non-zero for some $t > -2$, which is a contradiction.  Our assumption that the sequence $\theta_n$ exists must have been false.  The proposition must be true.  

\end{proof}


%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------

\section{A Decrease in Oscillation} \label{sec:harnack}

We put together Propositions \ref{thm:DG1} and \ref{thm:DG2} to produce an Oscillation lemma.  It allows us to improve a bound on the supremum of a function based on information about its positive support.  

\begin{proposition}[Oscillation Lemma] \label{thm:oscillation general}
Let $\kappa$, $\Comega$, and $\Cgamma$, be positive constants. Then there exists a constant $k_0>0$ such that the following holds:

Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  Assume that Lemma~\ref{thm:Caff Stinga representation} hold on $\Omega$ with kernels that satisfy
\[ K_{1/4}(x,y) \leq \Comega |x-y|^{1/2} K_{1}. \]

Let $\theta$, $\ulow$, $\uhigh$, $\Gamma$ and $\gamma$ solve \eqref{eq:main linear brokendown} on $[-2,0]\times\Omega$, and satisfy $\norm{\Lambda^{-1/4} \uhigh}_{L^\infty([-2,0]\times\Omega)} \leq 6 \kappa$, $\norm{\grad \ulow}_{L^\infty([-2,0]\times\Omega)} \leq 2\kappa$, and $\norm{\dot{\gamma}}_{L^\infty([-2,0])} \leq \Cgamma$.  


Suppose that for all $t \in [-5,0]$ and any $x \in \Omega$
\begin{equation} \label{oscillation boundedness} \theta(t,x) \leq 2 + 2^{-k_0} \paren{|x-\Gamma(t)|^{1/4}-2^{1/4}}_+, \end{equation}
and that
\[ \abs{\{\theta \leq 0\} \cap [-4,0]\times B_4(\Gamma)} \geq \frac{4|B_4|}{2}. \]

Then for all $t \in [-1,0]$, $x \in \Omega \cap B_1(\Gamma)$ we have
\[ \theta(t,x) \leq 2 - 2^{-k_0}. \]
\end{proposition}

\begin{proof}
Let $\mu$ and $\delta_0$ as in Proposition \ref{thm:DG2}, and take $k_0$ large enough that $(k_0-1) \mu > 4 |B_4|$.  

Consider the sequence of functions,
\[ \theta_k(t,x) := 2 + 2^k (\theta(t,x) - 2). \]
That is, $\theta_0 = \theta$ and as $k$ increases, we scale vertically by a factor of 2 while keeping height 2 as a fixed point.  Note that since $\theta$ satisfies \eqref{oscillation boundedness}, each $\theta_k$ for $k \leq k_0$ and $(t,x) \in [-5,0] \times \Omega$ satisfies
\[ \theta_k(t,x) \leq 2 + \paren{|x-\Gamma(t)|^{1/4}-2^{1/4}}_+. \]
This is precisely the assumption in Proposition \ref{thm:DG2}.  

Note also that
\begin{equation} \label{oscillation amount below} \abs{\{\theta_k \leq 0\} \cap [-4,0]\times B_4(\Gamma)} \end{equation}
is an increasing function of $k$, and hence is greater than $2|B_4|$ for all $k$.  

Assume, for means of contradiction, that
\begin{equation} \label{oscillation amount above} \abs{\{1 \leq \theta_k \} \cap [-2,0]\times B_2(\Gamma)} \geq \delta_0/4 \end{equation}
for $k = k_0-1$.  Since this quantity is decreasing in $k$, it must then exceed $\delta_0/4$ for all $ k < k_0$ as well.  

Applying Proposition \ref{thm:DG2} to each $\theta_k$, we conclude that 
\[ \abs{\{0 < \theta_k < 1\} \cap [-4,0]\times B_4(\Gamma)} \geq \mu. \]
In particular, this means that the quantity \eqref{oscillation amount below} increases by atleast $\mu$ every time $k$ increases by 1. By choice of $k_0$ and the fact that quantity \eqref{oscillation amount below} is trivially bounded by $4|B_4|$, we obtain a contradiciton.  Therefore, the assumption \eqref{oscillation amount above} must fail for $k = k_0-1$.  

Therefore $\theta_{k_0}$ must satisfy the assumptions of Proposition \ref{thm:DG1}.  In particular, we conclude that
\[ \theta_{k_0}(t,x) \leq 1 \qquad \forall t \in [-1,0], x \in \Omega \cap B_1(\Gamma). \]

For the original function $\theta$, this means that
\[ \theta(t,x) \leq 2 - 2^{-k_0} \qquad \forall t \in [-1,0], x \in \Omega \cap B_1(\Gamma). \]
\end{proof}

By assuming that $\theta$ is small near $x = \Gamma(t)$, we have shown that the oscillation of $\theta$ is decreased in a smaller neighborhood of $\Gamma(t)$.  However, our goal is to control the oscillation near $x = \Gamma(t) + \gamma(t)$.  Therefore we will prove the following proposition:

\begin{lemma}[Oscillation Lemma, with shift] \label{thm:oscillation shifted}
Let $\kappa$, $\Comega$, and $\Cgamma$, be positive constants, and let $k_0$ be as in Lemma~\ref{thm:oscillation general}.  Then there exists a constant $\lambda > 0$ such that the following holds:

Let $\Omega \subseteq \R^2$ be a bounded open set with $C^{2,\beta}$ boundary for some $\beta \in (0,1)$.  Assume that Lemma~\ref{thm:Caff Stinga representation} hold on $\Omega$ with kernels that satisfy
\[ K_{1/4}(x,y) \leq \Comega |x-y|^{1/2} K_{1}. \]

Let $\theta$, $\ulow$, $\uhigh$, $\Gamma$ and $\gamma$ solve \eqref{eq:main linear brokendown} on $[-5,0]\times\Omega$, and satisfy $\norm{\Lambda^{-1/4} \uhigh}_{L^\infty([-5,0]\times\Omega)} \leq 6 \kappa$, $\norm{\grad \ulow}_{L^\infty([-5,0]\times\Omega)} \leq 2\kappa$, and $\norm{\dot{\gamma}}_{L^\infty([-5,0])} \leq \Cgamma$.  

Suppose that for all $t \in [-5,0]$ and any $x \in \Omega$
\begin{equation} \label{theta bounded everywhere} |\theta(t,x)| \leq 2 + 2^{-k_0} \paren{|x-\Gamma(t)|^{1/4}-2^{1/4}}_+ \end{equation}
and that
\[ \abs{\{\theta \leq 0\} \cap [-4,0]\times B_4(\Gamma)} \geq 2|B_4|. \]

Then for any $\eps \in (0,1/5)$ such that
\begin{equation} \label{Cgamma and eps for harnack} 5 \Cgamma \leq \eps\n - 3 \end{equation}
we have
\[ \abs{\frac{2}{2-\lambda} \bracket{\theta(\eps t, \eps x) + \lambda}} \leq 2 + 2^{-k_0} \paren{|x-\eps\n\Gamma(\eps t)-\eps\n\gamma(\eps t)|^{1/4}-2^{1/4}}_+. \]
for all $t \in [-5,0]$ and $x$ such that $\eps x \in \Omega$.  
\end{lemma}

Before we can prove this, we state a technical lemma:



We are ready to prove Proposition~\ref{thm:oscillation shifted}.

The idea of the proof is to consider a small enough time interval that the difference between $\Gamma(t)$ and $\Gamma(t) + \gamma(t)$ is inconsequential.  However, considerable attention must be paid to the dependence of the parameters $\eps$, $\Cgamma$, and $k_0$.  Ostensibly, $k_0$ will depend on the constant $\Cgamma$ (since the value $\Cgamma$ is important in the proof of Lemma~\ref{thm:oscillation general} where $k_0$ is calculated) but in Section~\ref{sec:holder} we will actually define $\Cgamma$ in terms of the scaling parameter $\eps$, which means we cannot require $\eps$ to depend on $k_0$.  

The idea of the proof is to consider a small enough time interval that the difference between $\Gamma(t)$ and $\Gamma(t) + \gamma(t)$ is inconsequential.  However, special attention must be paid to the dependence of the parameters $\eps$, $\Cgamma$, and $k_0$.  The parameter $k_0$ (defined in Lemma~\ref{thm:oscillation general}) depends on $\Cgamma$.  In Section~\ref{sec:holder}, when we apply Lemma~\ref{thm:oscillation shifted} to the proof of Theorem~\ref{thm:main continuity}, we will actually define $\Cgamma$ in terms of the scaling parameter $\eps$.  Therefore in the following proof, where we define the the range of acceptable scaling parameters $\eps$, we shall strive to make those constraints depend as little as possible on $\Cgamma$ and $k_0$.  

If we only wish to show that by zooming horizontally by a large amount and zooming and translating vertically by a small amount we stay under the barrier, this is obvious and merely requires being written down.  Even the shift itself is clearly not a problem when considered in the un-zoomed coordinates.  Since the velocity of $\gamma$ is bounded by $\Cgamma$, the shift $\gamma$ is arbitrarily small over very small time periods.  The important thing to pay attention for is the dependence of $\eps$ and $\Cgamma$ and $k_0$ on eachother.  

As we will see in Section~\ref{sec:holder} when we apply this lemma, the constant $\Cgamma$ depends on $\eps$ and $k_0$ depends on $\Cgamma$.  In the following proof, the constant $\eps$ will need to be small relative to $\Cgamma$.  The assumption \eqref{Cgamma and eps for harnack} in this lemma turns out to be satisfiable, and now we must prove that it is sufficient.  

%from the fact that $k_0$ itself depends on $\Cgamma$, and as we will see in the next section $\Cgamma$ depends on $\eps$, so $\eps$ cannot depend on $k_0$.  In time, the co-dependence of $\eps$ and $\Cgamma$ is easy to untangle (so long as $\eps \Cgamma$ is less than some universal constant, the proof will go through).  In space, it is less clear that $\eps$ will not depend on $k_0$, and of course we need to zoom in time and space by the same factor so both issues are interconnected.  

\begin{proof}
Take $\lambda$ such that
\begin{equation} \label{lambda smallness assumptions} 2\lambda \leq 2^{-k_0}, \qquad (2+\lambda)(\frac{2}{2-\lambda}) \leq 2 + 2^{-k_0} \bar{\lambda}, \qquad \frac{2}{2-\lambda} \leq \alpha. \end{equation}
for $\bar{\lambda}>0$ and $\alpha>1$ from Lemma \ref{thm:technical scaling of barrier}.  

Denote 
\[ \bar{\theta}(t,x) := \frac{2}{2-\lambda} \bracket{\theta(\eps t, \eps x) + \lambda} \]
defined for $t \in [-5/\eps,0]$ and 
\[ x \in \Omega_\eps := \{x\in \R^2: \eps x \in \Omega\} \]
and denote
\[ \phi(x) := \paren{|x|^{1/4} - 2^{1/4}}_+. \]

We already proved in Lemma \ref{thm:oscillation general} that $\theta \leq 2 - 2^{-k_0}$ for $t \in [-1,0]$ and $x \in \Omega\cap B_1(\Gamma)$.  On this same set, $\theta \geq -2$ by assumption.  For $\bar{\theta}$, this means that when $t \in [-1/\eps, 0]$ and $x \in \Omega \cap B_{1/\eps}(\eps\n \Gamma(\eps t))$,
\begin{equation}\label{bar theta bounded basin} \begin{cases}
\bar{\theta}(t,x) &\leq \frac{2}{2-\lambda} \bracket{2-2^{-k_0}+\lambda} \leq \frac{2}{2-\lambda} \bracket{2-\lambda} = 2. \\
\bar{\theta}(t,x) &\geq \frac{2}{2-\lambda} \bracket{-2+\lambda} = -2.
\end{cases} \end{equation}

Similarly, the bound \eqref{theta bounded everywhere} on $\theta$ becomes the equivalent bounds on $\bar{\theta}$, for all $(t,x) \in [-5/\eps,0] \times \Omega_\eps$
\begin{equation} \bar{\theta}(t,x) \leq \frac{2}{2-\lambda} \bracket{2 + \lambda + 2^{-k_0} \phi(|\eps x - \Gamma(\eps t)|)} \label{bar theta bounded above everywhere} \end{equation}
and
\begin{equation} \bar{\theta}(t,x) \geq \frac{2}{2-\lambda} \bracket{- 2 + \lambda - 2^{-k_0} \phi(|\eps x - \Gamma(\eps t)|)}. \label{bar theta bounded below everywhere} \end{equation}

It remains to show that these bounds \eqref{bar theta bounded basin}, \eqref{bar theta bounded above everywhere}, and \eqref{bar theta bounded below everywhere} on $\bar{\theta}$ imply the bound stipulated by the proposition.  

Let $t \in [-5,0]$ and $x \in \Omega_\eps$, and define 
\[ y := x - \eps\n \Gamma(\eps t). \]

From \eqref{bar theta bounded above everywhere} and the assumptions \eqref{lambda smallness assumptions}, we can bound
\begin{align*} 
\bar{\theta}(t,x) &\leq \frac{2}{2-\lambda} \bracket{2 + \lambda + 2^{-k_0} \phi(\eps |y|)}
\\ &\leq 2 + 2^{-k_0} \bar{\lambda} + 2^{-k_0} \alpha \phi(\eps |y|)
\\ &= 2 + 2^{-k_0} \bracket{\bar{\lambda} + \alpha \phi(\eps |y|)}.
\end{align*}

From \eqref{bar theta bounded below everywhere} and the assumptions \eqref{lambda smallness assumptions}, we can bound
\begin{align*}
-\bar{\theta}(t,x) &\leq \frac{2}{2-\lambda} \bracket{2 -\lambda + 2^{-k_0} \phi(\eps |y|)}
\\ &\leq 2 + 2^{-k_0} \alpha \phi(\eps |y|)
\\ &\leq 2 + 2^{-k_0} \bracket{\bar{\lambda} + \alpha \phi(\eps |y|)}.
\end{align*}

Therefore
\begin{equation} \label{bar theta bounded everywhere} \abs{\bar{\theta}(t,x)} \leq 2 + 2^{-k_0} \bracket{\bar{\lambda} + \alpha \phi(\eps |y|)}. \end{equation}

If $|y| \leq \eps\n$ then from \eqref{bar theta bounded basin} we have
\[ \abs{\bar{\theta}(t,x)} \leq 2 \leq 2 + 2^{-k_0} \phi(x - \eps\n \Gamma(\eps t) - \eps\n \gamma(\eps t)) \]
and the proof would be complete.  Therefore assume without loss of generality that $|y|\geq \eps\n$.  In this case we can apply Lemma \ref{thm:technical scaling of barrier} which states that, since $\eps<1/2$ and $\eps|y| \geq 1$, it is a property of $\phi$, $\alpha$, and $\bar{\lambda}$ that
\[ 2 + 2^{-k_0} \bracket{\bar{\lambda} + \alpha \phi(\eps |y|)} \leq 2 + 2^{-k_0} \bracket{\phi(|y|-\eps\n + 3)}. \]

For $t \in [-5,0]$, we have by assumption \eqref{Cgamma and eps for harnack}
\[ |y|-\eps\n+3 \leq |y| - 5 \Cgamma \leq |y - \eps\n\gamma(\eps t)|. \]

The estimate \eqref{bar theta bounded everywhere} becomes
\[ \abs{\bar{\theta}(t,x)} \leq 2 + 2^{-k_0} \phi(|x - \eps\n\Gamma(\eps t) - \eps\n\gamma(\eps t)|). \]

This concludes the proof.  
\end{proof}

%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------

\section{H\"{o}lder Continuity} \label{sec:holder}

In this section we shall prove the main theorem, Theorem~\ref{thm:main continuity}.  We begin with a final lemma to describe the scaling properties of \eqref{eq:main linear}.  

\begin{lemma}[Scaling] \label{thm:scaling}
Let $\Omega \subseteq \R^2$ be a bounded set with $C^{2,\alpha}$ boundary.  Suppose that $\theta:[-T,0] \times \Omega \to \R$ and $u:[-T,0]\times \Omega \to \R^2$ solve \eqref{eq:main linear} and $u$ satisfies
\[ u = \sum_{j=j_0}^\infty u_j \]
with that sum converging in $L^2(\Omega)$ and $(u_j)_j$ calibrated with constant $\kappa$ and center $N$.  Suppose that on $\Omega$ the functions $K_{1/4}$ and $K_1$ (defined in Proposition~\ref{thm:Caff Stinga representation}) satisfy the relation
\begin{equation} \label{scaling 1/4 to 1 property} K_{1/4}(x,y) \leq \Comega |x-y|^{3/4} K_1(x,y) \qquad \forall x\neq y \in \Omega. \end{equation}

Let $\eps>0$ be a small constant. 

Then
\[ \bar{\theta}(t,x) := \theta(\eps t, \eps x) \]
and
\[ \bar{u}(t,x) := \sum_{j=j_0}^\infty u_j(\eps t, \eps x) \]
satisfies the same PDE on $[-T/\eps, 0]\times \Omega_\eps$ where $\Omega_\eps = \{x \in \R^2: \eps x \in \Omega\}$.  

Moreover, $(u_j)_j$ is calibrated with the same constant $\kappa$ but with center $N - \log_2(\eps)$, and the estimate
\[ \bar{K}_{1/4}(x,y) \leq \Comega |x-y|^{3/4} \bar{K}_1(x,y) \qquad \forall x\neq y \in \Omega_\eps \]
holds.  

%\[ \norm{\sum_{j=-\infty}^0 \bar{u}_j(t,0) - \sum_{j=-\infty}^0 u_j(\eps t, 0)}_\infty \leq \kappa N. \]
\end{lemma}

\begin{proof}
Denote by $\bar{\Lambda}$ the square root of the Laplacian with Dirichlet boundary conditions on $\Omega_\eps$.  One can calculate (see e.g. \cite{CaSt} Section 2.4) that for $(t,x) \in [-T/\eps, 0]\times \Omega_\eps$
\[ \Lambda \theta(\eps t,\eps x) = \eps \bar{\Lambda} \bar{\theta}(t,x). \]

Similarly, in the Caffarelli-Stinga representation from Proposition~\ref{thm:Caff Stinga representation} the operator $\bar{\Lambda}^s$ will have kernel
\[ \bar{K}_s(x,y) = \eps^s K_s(\eps x,\eps y). \]

From these facts it is clear that the scaled functions satisfy \eqref{eq:main linear} and \eqref{scaling 1/4 to 1 property}.  

%We calculate
%\[ \del_t \bar{\theta}(p) = \eps \del_t \theta(\bar{p}) \]
%and 
%\[ \grad \bar{\theta}(p) = \eps \grad \theta(\bar{p}) \]
%and
%\[ \Lambda \bar{\theta}(p) = \eps \Lambda \theta(\bar{p}). \]
%
%\& cetera...

Define
\[ \bar{u}_j(t,x) := u_j(\eps t, \eps x). \]
To show that $(\bar{u}_j)_{j \in \Z}$ is calibrated, we must translate the various bounds on $u_j$ to corresponding bounds on $\bar{u}_j$.  Each of the calculations are similar, so we show only one:
\[ \norm{\grad \bar{u}_j}_\infty = \eps \norm{\grad u_j}_\infty \leq 2^{\log_2(\eps)} 2^j 2^{-N} \kappa = 2^j 2^{-(N-\log_2(\eps))} \kappa. \]

\end{proof}


\begin{proof}[Proof of Theorem \ref{thm:main continuity}]
By Proposition~\ref{thm:L2 to Linfty}, the $L^\infty$ norm of $\theta$, after a short time, will be bounded by $\norm{\theta_0}_{L^2}$.  By translating and scaling, it will be sufficient to assume that $\theta$ solving \eqref{eq:main nonlinear} satisfies
\[ \norm{\theta}_{L^\infty([-5,0] \times \Omega)} \leq 2 \]
and prove that $\theta$ is H\"{o}lder continuous at the origin $(0,0) \in [-5,0]\times\bar{\Omega}$, meaning
\[ \frac{|\theta(t,x) - \theta(0,0)|}{\paren{|t|^2 + |x|^2}^{\alpha/2}} \leq C \]
for all $(t,x) \in [-5,0]\times\Omega$ and some constants $\alpha$ and $C$ depending on $\Omega$.  
% Thus, by translating and scaling, one can assume without loss of generality that 
%We will show that $\theta$ is H\"{o}lder continuous at the origin $(0,0) \in [-5,0]\times\bar{\Omega}$ and, by translation invariance, the theorem will follow.  

%We'll show that if $\theta$ with $\norm{\theta}_{L^\infty([-5,0] \times \Omega)} \leq 2$ solves \eqref{eq:main nonlinear} on $[-5,0]\times \Omega$ then $\theta$ is H\"{o}lder continuous at the point $(0,0)$ (with possibly $0 \in \bar{\Omega}$).  Up to translation and scaling, this will be sufficient to show continuity at all points in the domain.  

From Proposition~\ref{thm:u is calibrated}, we know that 
\[ u = \grad^\perp \Lambda^{-1} \theta = \sum_{j=j_0}^\infty u_j \]
for a sequence $(u_j)_{j\geq j_0}$ of divergence-free functions calibrated with some constant $\kappa = \kappa(\Omega)$ and center 0.  

Choose a constant $0 < \eps < 1/5$ such that
\begin{equation}\label{eps is small enough for Cgamma} 
5 \max\paren{ - \kappa \log_2(\eps) e^{10\eps\kappa}, (1-j_0) \kappa} \leq \eps\n - 3,
\end{equation}

%\[ 5 \max\paren{ - \kappa \log_2(\eps) e^{10\eps\kappa}, (1-j_0) \kappa} \leq \eps^{-a k}/k \qquad \forall k\geq 0. \]
%critical point at $k = -1/(a \ln(\eps))$, at that point the bound is $\leq -a \ln(\eps) \eps^{1/\ln(\eps)} = - a \ln(\eps) e$

For notational convenience, denote
\[ \sum_k = \sum_{j > - k \log_2(\eps)}, \qquad \sum^k = \sum_{j \leq -k \log_2(\eps)}. \]

For integers $k \geq 0$ consider the domains
\[ \Omega_k := \{x \in \R^2: \eps^k x \in \Omega\} \]
and define the following functions on $[-5,0]\times \Omega_k$:
\begin{align*} 
\ulowth{k}(t,x) &:= \sum^k u_j(\eps^k t, \eps^k x), \\
\uhighth{k}(t,x) &:= \sum_k u_j(\eps^k t, \eps^k x).  
\end{align*}
By Lemmas \ref{thm:scaling} and \ref{thm:calibration is good}, we know the sequence $(u_j(\eps^k \cdot, \eps^k \cdot))_j$ is calibrated and hence that independently of $k$
\[ \norm{\Lambda^{-1/4} \uhighth{k}}_{L^\infty([-5,0]\times \Omega_k)} \leq 6 \kappa \]
and
\[ \norm{\grad \ulowth{k}}_{L^\infty([-5,0]\times \Omega_k)} \leq 2 \kappa. \]
Each $\ulowth{k}$ is a finite sum of $L^\infty$ functions, hence $L^\infty$ itself, though not uniformly in $k$.  
\vskip.3cm

For $t \in [-5,0]$ and $k \geq 0$ define $\Gamma_k, \gamma_k: [-5,0] \to \R^2$ by the following ODEs:
\begin{align*}
\Gamma_0(t) &:= 0, \\
\gamma_k(0) &:= 0, \\
\dot{\gamma}_k(t) &:= \ulowth{k}(t, \Gamma_k(t) + \gamma_k(t)) - \dot{\Gamma}_k(t) \\
\Gamma_k(t) &:= \eps\n \gamma_{k-1}(\eps t) + \eps^{-2} \gamma_{k-2}(\eps^2 t) + \cdots + \eps^{-k} \gamma_0(\eps^k t), \qquad k \geq 1.
\end{align*}
Since each $\ulowth{k}$ is $L^\infty$ in space-time and Lipschitz in space, these $\gamma_k$ exist by a variant of the Cauchy-Lipschitz theorem.  For example, Theorem 3.7 of \cite{BaChDa} proves existence and uniqueness in our case.  Moreover, since $\ulowth{k}$ is a vector field which is tangential to the boundary of $\Omega_k$ and it has unique flows, the path $\Gamma_k + \gamma_k$ which follows this vector field must remain inside $\Omega_k$ for all time and so our expressions remain well-defined.  

%Each $\ulowth{k}$ is a Lipschitz vector field, and each $\Gamma_k + \gamma_k$ is a flow along that vector field which ends at the origin at $t=0$.  In particular, since  $\ulowth{k}$ is tangential to the boundary of $\Omega_k$ and has unique flows, the flow $\Gamma_k + \gamma_k$ cannot exit the region $\Omega_k$ and so our expressions remain well-defined.  



%I want to claim that 
%\[ \dot{\Gamma}_k(t) = \sum^{k-1} (\eps^k t, \eps^k \Gamma_k(t)). \]

%Notice that $\dot{\gamma}_0(t) = \ulowth{0}(t,\Gamma_0(t) + \gamma_0(t))$.  
By construction, for $k \geq 0$ we have $\Gamma_{k+1}(t) = \eps\n \gamma_k(\eps t) + \eps\n \Gamma_k(\eps t)$.  Therefore
\begin{align*} 
\dot{\Gamma}_{k+1}(t) &= \del_t \bracket{\eps\n \gamma_k(\eps t) + \eps\n \Gamma_k(\eps t)}
\\ &= \dot{\gamma}_k(\eps t) + \dot{\Gamma}_k(\eps t)
\\ &= \ulowth{k}(\eps t, \gamma_k(\eps t) + \Gamma_k(\eps t))
\\ &= \ulowth{k}(\eps t, \eps \Gamma_{k+1}(t)).  
\end{align*}

%Well, $\dot{\gamma}_0(t) = \ulowth{0}(t,\gamma_0(t))$.  Moreover, 
%\[ \ulowth{k}(t,\Gamma_{k+1}(t)) = \ulowth{k}(\eps\n \eps t, \eps\n \bracket{\gamma_k(\eps t) + \Gamma_k(\eps t)}) \]
%or
%\begin{align*} 
%\sum^k u_j(\eps^{k+1} t, \eps^{k+1} \Gamma_{k+1}(t)) &= \sum^k u_j(\eps^k \eps t, \eps^k \bracket{\gamma_k(\eps t) + \Gamma_k(\eps t)})
%\\ &= \ulowth{k}(\eps t, \gamma_k(\eps t) + \Gamma_k(\eps t))
%\\ &= \dot{\gamma}_k(\eps t) + \dot{\Gamma}_k(\eps t)
%\\ &= \del_t \bracket{\eps\n \gamma_k(\eps t) + \eps\n \Gamma_k(\eps t)}
%\\ &= \dot{\Gamma}_{k+1}(t).
%\end{align*}
%
%In other words,
%\[ \dot{\Gamma}_k(t) = \sum^{k-1} u_j(\eps^k t, \eps^k \Gamma_k(t)) \qquad k \geq 2. \]

With this in hand, we can bound the size of $\gamma_k$.  Namely, for $k \geq 1$, 
\begin{align*}
\dot{\gamma}_k(t) &= \ulowth{k}(t, \Gamma_k(t) + \gamma_k(t)) - \dot{\Gamma}_k(t)
\\ &= \ulowth{k}(t, \Gamma_k(t) + \gamma_k(t)) - \ulowth{k-1}(\eps t, \eps \Gamma_k(t))
\\ &= \sum^k u_j(\eps^k t, \eps^k \Gamma_k(t) + \eps^k \gamma_k(t)) - \sum^{k-1} u_j(\eps^k t, \eps^k \Gamma_k(t))
\\ &= \sum^{k-1} \bracket{u_j(\eps^k t, \eps^k \Gamma_k(t)+\eps^k \gamma_k(t)) - u_j(\eps^k t, \eps^k \Gamma_k(t))} + \sum_{k-1}^k u_j(\eps^k t, \eps^k \ldots)
\\ &= \bracket{\ulowth{k-1}\big(\eps t, \eps \Gamma_k(t)+\eps \gamma_k(t)\big) - \ulowth{k-1}(\eps t, \eps \Gamma_k(t))} + \sum_{k-1}^k u_j(\eps^k t, \eps^k \ldots).
\end{align*}
The function $x \mapsto \ulowth{k-1}(\eps t, \eps x)$ is Lipschitz, with Lipschitz constant less than $2 \eps \kappa$.  Moreover, each $u_j$ has $\norm{u_j}_\infty \leq \kappa$.  Thus from the above calculation we can bound
\begin{equation} \label{ODE for dot gamma} |\dot{\gamma}_k(t)| \leq 2 \eps \kappa |\gamma_k(t)| - \kappa \log_2(\eps). \end{equation}
Applying Gronwall's inequality, we find that for $t \in [-5,0]$
\[ |\gamma_k(t)| \leq \frac{-\log_2(\eps)}{2 \eps} \paren{ e^{10 \eps \kappa} - 1}. \]
Plugging this estimate back into \eqref{ODE for dot gamma},
\[ |\dot{\gamma}_k(t)| \leq -\kappa \log_2(\eps) e^{10\eps \kappa} \qquad \forall k \geq 1. \]

Trivially $|\dot{\gamma}_0| \leq (j_0-1) \kappa$, so if we define
\[ \Cgamma = \max\paren{ - \kappa \log_2(\eps) e^{10\eps\kappa}, (j_0-1) \kappa} \]
then for all $k \geq 0$ and $t \in [-5,0]$
\[ |\dot{\gamma}_k(t)| \leq \Cgamma. \]
\vskip.3cm

Let us now produce a sequence of solutions $\theta_k$.  Define
\[ \theta_0(t,x) := \theta(t,x) \]
and for each $k \geq 0$, if $|\{\theta_k \leq 0\} \cap [-5,0]\times B_4(\Gamma_k(t))| \geq 2|B_4|$ then set
\[ \theta_{k+1}(t,x) := \frac{2}{2-\lambda} \bracket{\theta_k(\eps t, \eps x) + \lambda}. \]
Otherwise, set
\[ \theta_{k+1}(t,x) := \frac{1}{1-\lambda} \bracket{\theta_k(\eps t, \eps x) - \lambda}. \]

From Lemma \ref{thm:scaling}, we know that $\theta_k$ and the calibrated sequence $(u_j(\eps^k \cdot, \eps^k \cdot))_j$ solve \eqref{eq:main linear}.  
\vskip.3cm

We will now show that
\begin{equation}\label{thetak below the barrier}
|\theta_k| \leq 2 + 2^{-k_0} \paren{|x-\Gamma_k(t)|^{1/4} - 2^{1/4}}_+
\end{equation}
holds for all $k \geq 0$.  

Since $|\theta_0|\leq 2$ by assumption, we know in particular that \eqref{thetak below the barrier} holds at $k=0$.  

This is sufficient for us to apply Lemma \ref{thm:oscillation shifted} to each $\theta_k$ (or to $-\theta_k$ as appropriate) in order.  We conclude that \eqref{thetak below the barrier} holds for all $k \geq 0$.  
%\[ \abs{\theta_{k+1}(t,x)} \leq 2 + 2^{-k_0} \paren{|x-\Gamma_{k+1}(t)|^{1/4} - 2^{1/4}}_+. \]

Each $\theta_k$ is between $-2$ and 2 on $[-5,0]\times B_2(\Gamma_k)$.  But recall that each $\Gamma_k$ is Lipschitz with constant $k \Cgamma$.  Thus $|\Gamma_k(t)|\leq 1$ for $t \in [-(k \Cgamma)\n, 0]$.  On that time interval, 
\[ \abs{\theta_k(t,x)} \leq 2 \qquad \forall x \in B_1(0). \]

We conclude that
\[ \abs{ \sup_{[-\eps^k (k \Cgamma)\n, 0] \times B_{\eps^k}(0)} \theta(t,x) - \inf_{[-\eps^k (k \Cgamma)\n, 0] \times B_{\eps^k}(0)} \theta(t,x) } \leq 4 \paren{\frac{2}{2-\lambda}}^{-k}. \]

In particular, for some positive constant $C$ such that
\[ \eps^{C k} \leq (k \Cgamma)\n \qquad \forall k \geq 0, \]
we can say that
\[ |t|^2 + |x|^2 \leq \eps^{(1+C)k} \]	
implies that $(t,x) \in [-\eps^k (k \Cgamma)\n, 0] \times B_{\eps^k}(0)$ which in turn implies that
\[ \abs{\theta(t,x) - \theta(0,0)} \leq  4 \paren{\frac{2}{2-\lambda}}^{-k}. \]

In other words,
\begin{align*} 
\abs{\theta(t,x) - \theta(0,0)} &\leq 4 \paren{\frac{2}{2-\lambda}}^{ -\frac{1}{1+C} \log_\eps(|t|^2 - |x|^2)  + 1} 
\\ &= 4 \paren{\frac{2}{2-\lambda}} \exp\bracket{\ln\paren{\frac{2}{2-\lambda}} \frac{\ln(|t|^2 + |x|^2)}{-(1+C)\ln(\eps)}}
\\ &= \frac{8}{2-\lambda} (|t|^2 + |x|^2)^{-\frac{\ln(2) - \ln(2-\lambda)}{(1+C)\ln(\eps)}}.
\end{align*}

\end{proof}

%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------


\appendix
\section{Technical Lemmas} \label{sec:technical}

In this appendix we state and prove a few technical lemmas.  

%\label{thm:Holder interpolation}

\begin{lemma} \label{thm:interpolation C1 to holder}
Let $\alpha \in (0,1)$.  There exists a constant $C = C(\alpha)$ such that, for any set $\Omega$ and any $f \in C^{0,1}(\Omega)$,
\[ \bracket{f}_\alpha \leq C \norm{f}_\infty^{1-\alpha} \norm{\grad f}_\infty^\alpha. \]
\end{lemma}

\begin{proof}
This simple lemma is a straightforward calculation:
\begin{align*} 
\sup_{x,y \in \Omega} \frac{|f(x)-f(y)|}{|x-y|^\alpha} &= \sup |f(x)-f(y)|^{1-\alpha} \paren{\frac{|f(x)-f(y)|}{|x-y|}}^\alpha 
\\ &\leq \paren{2 \norm{f}_\infty}^{1-\alpha} \paren{ \sup \frac{|f(x)-f(y)|}{|x-y|} }^\alpha
\\ &\leq C \norm{f}_\infty^{1-\alpha} \norm{\grad f}_\infty^\alpha.
\end{align*}
\end{proof}

\begin{lemma} \label{thm:interpolation holder to C1}
Let $\alpha \in (0,1)$ and $\Omega$ a set that satisfies the cone condition.  There exist constants $C = C(\alpha, \Omega)$ and $\ell = \ell(\Omega)$ such that, for any $f \in C^{2,\alpha}(\Omega)$
\[ \norm{D^2 f}_\infty \leq C \paren{ \delta\n \norm{\grad f}_\infty  + \delta^\alpha \bracket{D^2 f}_\alpha }\]
for all $\delta < \ell$.  
\end{lemma}

\begin{proof}
We will prove the stronger claim that for $f \in C^{1,\alpha}$
\[ \norm{\grad f}_\infty \leq C \delta\n \norm{f}_{L^\infty(\bar{\Omega})} + \delta^\alpha \bracket{\grad f}_{\alpha;\bar{\Omega}}.\]

The idea of the proof is to average $\grad f$ along an interval of length $\delta$ with endpoint $x$.  The magnitude of the average will be small, since $f \in L^\infty$, and the average will differ not very much from $\grad f(x)$ since $\grad f \in C^{1,\alpha}$.  

Since $\Omega$ satisfies the cone condition, there exist positive constants $\ell$ and $a<1$ such that, at each point $x \in \bar{\Omega}$, there exist two unit vectors $e_1$ and $e_2$ such that $|e_1\cdot e_2| \leq a$ and $x + \tau e_i \in \Omega$ for $i=1,2$ and $0 < \tau \leq \ell$.  In other words, $\Omega$ contains rays at each point that extend for length $\ell$, end at $x$, and are non-parallel with angle at least $\cos\n(a)$.  

Consider the directional derivative $\del_i f$ of $f$ along the direction $e_i$, and observe that for any $0 < \delta \leq \ell$,
\begin{equation} \label{average bounded by Linfty} \abs{\int_0^\delta \del_i f(x + \tau e_i) \,d\tau} = \abs{f(x+\delta e_i) - f(x)} \leq 2 \norm{f}_\infty. \end{equation}

On the other hand, $\del_i f$ is continous so, for any $\tau \in (0,\ell]$,
\[ \abs{\del_i f(x) - \del_i f(x+\tau e_i)} \leq \bracket{\grad f}_\alpha \tau^\alpha. \]
From this, we obtain that
\[ \int_0^\delta \del_i f(x + \tau e_i) \,d\tau \leq \int_0^\delta \paren{\del_i f(x) + \bracket{\grad f}_\alpha \tau^\alpha } \,d\tau = \delta \del_i f(x) + \bracket{\grad f}_\alpha \frac{\delta^{1+\alpha}}{1+\alpha} \]
and a similar bound holds from below.  Thus
\[ \abs{ \delta \del_i f(x) - \int_0^\delta \del_i f(x + \tau e_i) \,d\tau} \leq \bracket{\grad f}_\alpha \frac{\delta^{1+\alpha}}{1+\alpha}. \]

Combining this bound with \eqref{average bounded by Linfty}, we obtain
\[ \abs{\del_i f(x)} \leq \frac{2}{\delta} \norm{f}_\infty + \frac{\delta^\alpha}{1+\alpha} \bracket{\grad f}_\alpha. \]

This bound is independent of $x$ and of $i=1,2$.  Since $e_1 \cdot e_2 \leq a$ by assumption, by a little linear algebra we can bound $\grad f$ in terms of the $\del_i f$ and obtain that, for all $\delta \in (0,\ell]$,
\[ \norm{\grad f}_\infty \leq \frac{C}{1-a^2} \paren{ \delta\n \norm{f}_\infty + \delta^\alpha \bracket{\grad f}_\alpha }. \]

\end{proof}



\begin{lemma} \label{thm:technical scaling of barrier}
There exist constants $\bar{\lambda} > 0$ and $\alpha > 1$ such that, for any $0 < \eps \leq 1/2$ and any $z \geq 1$
\[ \paren{|\eps\n (z - 1) + 3|^{1/4} - 2^{1/4}}_+ - \alpha \paren{|z|^{1/4} - 2^{1/4}}_+ \geq \bar{\lambda}. \]
\end{lemma}

\begin{proof}
For $z$ fixed, this function is increasing as $\eps$ decreases, so it will suffice to show the lemma when $\eps = 1/2$, that is to show
\[ f_\alpha(z) := \paren{|2 z + 1|^{1/4} - 2^{1/4}}_+ - \alpha \paren{|z|^{1/4} - 2^{1/4}}_+ \geq \bar{\lambda} \]
for all $z \geq 1$.  Note that $f_\alpha(z) \geq f_\beta(z)$ if $\alpha < \beta$.  

For $z \geq 2$, 
\[ f_\alpha(z) = (2z+1)^{1/4} - 2^{1/4} - \alpha z^{1/4} + \alpha 2^{1/4} = z^{1/4} \paren{(2 + 1/z)^{1/4} - \alpha} + (\alpha-1)2^{1/4}. \]
For any $\alpha < 2^{1/4}$, clearly $f_\alpha(z)$ tends to $\infty$ as $z$ increases. Therefore there exist $N$ and $\alpha_0 > 1$ such that 
\[ f_\alpha(z) \geq 1 \qquad \forall z \geq N, \alpha\leq \alpha_0. \]
\vskip.3cm

We can decompose $f_\alpha(z) = g_1(z) - (\alpha - 1) g_2(z)$ where
\begin{align*} 
g_1(z) &:= \paren{|2 z + 1|^{1/4} - 2^{1/4}}_+ - \paren{|z|^{1/4} - 2^{1/4}}_+, \\
g_2(z) &:= \paren{|z|^{1/4} - 2^{1/4}}_+. 
\end{align*}
Note that $g_1$, $g_2$ are both continuous, and $g_1(z)$ is strictly positive for $z \geq 1$.  Therefore we can take $\alpha \in (1,\alpha_0]$ small enough that
\[ \alpha - 1 < \frac{\inf_{[1,N]} g_1}{\sup_{[1,N]} g_2}. \]

For this $\alpha$, $f_\alpha(z)$ is strictly positive on the compact interval $[1,N]$, and $f_\alpha(z) \geq 1$ on $[N,\infty)$.  Therefore $f_\alpha(z)$ has a positive lower bound $\bar{\lambda}$ for all $z \geq 1$.  
\end{proof}

%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------

%\section{Existence} \label{sec:existence}
%In \cite{CoIg.sqg}, appendix 2, it is argued that for initial data $\theta_0 \in H_0^1(\Omega) \cap H^2(\Omega)$, there exist local-in-time solutions to \eqref{eq:main nonlinear} with
%\[ \theta \in L^\infty(0, T; H_0^1(\Omega)  H^2(\Omega)) \cap L^2(0,T; \HD^{2.5}). \]
%
%In particular, this is enough to show that $\theta \in L^\infty(0,T; L^4(\Omega))$ and hence that $u$ is as well.  Therefore the drift term $u \cdot \grad \theta$ is a product of an $L^2$ function and an $L^4$ function.  
%
%This is enough to justify all of the calculations in the present paper of the form
%\[ 0 = \int \varphi (\theta - \Psi)_+ \bracket{\del_t \theta + u \cdot \grad\theta + \Lambda \theta} \,dx \]
%for $\varphi$ an $L^\infty$ function and $\Psi$ a non-negative function.  
%
%Given $L^2(\Omega)$ initial data $\theta_0$, one can prove existence for a H\"{o}lder continuous solution on an interval $[0,T]$ by approximating $\theta_0$ by a sequence of sufficiently regular functions.  For this sequence, we apply the local existence theory and the H\"{o}lder theory to construct uniformly H\"{o}lder continuous solutions over the entire time interval $[0,T]$.  One can then use Arzela-Ascoli to construct a limit, which will be both a weak solution to \eqref{eq:main nonlinear} and a H\"{o}lder continuous function with slightly lower exponent.  

%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------%-------

%\section{Waxing Philosophical}
\bibliographystyle{alpha}
\bibliography{SQG-references}

\end{document}